---
title: "Memo - "
output: html_notebook
date: "2/2/2021"
---

```{r setup, include=FALSE}
source("../../code/0-setup/1-setup.R")
library("patchwork")
```

```{r data_input, include=FALSE}
aqs_sites <- readRDS("../../data/interim/aqs_sites.rds")
aqs_daily_annuli_preproduction <- 
  readRDS("../../data/processed/aqs_daily_annuli_preproduction.rds")
#aqs_daily_annuli_production <-  # need to make and export this dataset
#  readRDS("../../data/processed/aqs_daily_annuli_production.rds")
```


## Objectives

In this memo, we visualize the time series of data for several monitors in the dataset.


## Monitor

Monitors near wells with PM2.5 observations: 060210003 (Glenn County), 060374002 (LA County), 060374004 (LA County)

### Monitor 060374004

This monitor is located in the Los Angeles County, has at least one day of exposure to preproduction wells within 2 km, and PM2.5 data.



### Monitor 060290232

This monitor is located in the San Joaquin Valley and has at least one day of exposure to preproduction wells within 1 km.

```{r include=FALSE}
monitor <- aqs_daily_annuli_preproduction %>%
  filter(monitor_id == "060290232") %>%
  filter(year %in% c(2011:2015)) %>%  # these with preprod wells nearby
  mutate(preprod_count_within_3km = (preprod_count_uw_0to1km +
                                       preprod_count_uw_1to2km +
                                       preprod_count_uw_2to3km)) %>%
  # standardizes pollutants
  mutate(pm10_std = (pm10_mean / mean(pm10_mean, na.rm = T)),
         o3_std = (o3_max / mean(o3_max, na.rm = T))) %>%
  mutate(pm10_std = (pm10_std - mean(pm10_std, na.rm = T)),
         o3_std = (o3_std - mean(o3_std, na.rm = T))) %>%
  # standardizes covariates
  mutate(precip_std = (narr_precip / mean(narr_precip, na.rm = T)),
         temp_std = (narr_temp / mean(narr_temp, na.rm = T))) %>%
  mutate(precip_std = (precip_std - mean(precip_std, na.rm = T)),
         temp_std = (temp_std - mean(temp_std, na.rm = T)))
```


```{r include=FALSE}
# makes dataset with PM2.5 residuals and covariates
data_pm25 <- aqs_daily_annuli_preproduction %>%
  filter(pm25_mean >= 0) %>%
  mutate(preprod_count_within_3km = (preprod_count_uw_0to1km +
                                       preprod_count_uw_1to2km +
                                       preprod_count_uw_2to3km))
model_fit <- felm(pm25_mean ~ 
                    n_plume +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed |
                    factor(day_of_week) +
                    factor(carb_basin):factor(month) +
                    factor(carb_basin):factor(year),
                  data = subset(aqs_daily_annuli_preproduction,
                                pm25_mean >= 0))
data_pm25$residuals <- as.numeric(residuals(model_fit))
```


#### Plot. Time series of PM2.5 residuals at monitor 060374002 (LA county)

```{r include=FALSE}
panel_a <- data_pm25 %>%
  filter(monitor_id == "060374002") %>%
  filter(year %in% c(2010:2015)) %>% 
  ggplot() +
  geom_point(aes(date, residuals), alpha = 0.1) +
  theme_classic() +
  labs(x = "", y = "PM2.5 Residuals") +
  theme(axis.line.x  = element_blank(),  # removes x-axis
        axis.ticks.x = element_blank(),
        axis.text.x  = element_blank())
```

```{r include=FALSE}
panel_b <- data_pm25 %>%
  filter(monitor_id == "060374002") %>%
  filter(year %in% c(2010:2015)) %>%
  ggplot() +
  geom_area(aes(date, preprod_count_within_3km)) +
  labs(x = "Date", y = "n") +
  theme_classic()
```

```{r echo=FALSE, warning=FALSE}
figure <- panel_a / panel_b
figure
ggsave(filename = "time_series_monitor_060374002.png", plot = figure, device = "png",
       height = 3, width = 4,
       path = "../../output/figures/supplemental/")
```

#### Plot. Residuals x Preprod Count (1-2 km)

```{r echo=FALSE}
data_pm25 %>%
  #filter(monitor_id %in% c("060374004", "060374002", "060210003")) %>%
  #mutate(preprod_count_uw_0to3 = (preprod_count_uw_0to1km +
  #                                  preprod_count_uw_1to2km + 
  #                                  preprod_count_uw_2to3km)) %>%
  ggplot(aes(preprod_count_uw_1to2km, residuals)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(color = monitor_id), alpha = 0.1) +
  geom_smooth(method = lm, formula = y ~ x) +
  ylim(-10, 30) +
  theme_classic() +
  theme(legend.position = "none")
```


#### Plot. Residuals x Preprod Count (2-3 km)

```{r echo=FALSE}
data_pm25 %>%
  #filter(monitor_id %in% c("060374004", "060374002", "060210003")) %>%
  #mutate(preprod_count_uw_0to3 = (preprod_count_uw_0to1km +
  #                                  preprod_count_uw_1to2km + 
  #                                  preprod_count_uw_2to3km)) %>%
  ggplot(aes(preprod_count_uw_2to3km, residuals)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(color = monitor_id), alpha = 0.1) +
  geom_smooth(method = lm, formula = y ~ x) +
  theme_classic() +
  theme(legend.position = "none")
```