---
title: "Memo - Wind direction randomization"
output: html_notebook
date: "01/27/2021"
---

## Objectives

This memo examines whether randomization was successful 


```{r setup, include=FALSE}
source("../../code/0-setup/1-setup.R")
```

```{r input_data, include=FALSE}
aqs_sites <- readRDS("../../data/interim/aqs_sites.rds")
aqs_daily_annuli_random_wind <- 
  readRDS("../../data/processed/aqs_daily_annuli_preproduction.rds") %>%
  select(monitor_day, monitor_id, carb_basin, narr_wind_direction, narr_wind_speed) %>%
  mutate(wind_direction_random = runif(1621240, 0, 360))
```


## Visualizations

#### Plot. Distribution of random wind direction vector

```{r echo=FALSE}
aqs_daily_annuli_random_wind %>%
  ggplot() +
  geom_histogram(aes(wind_direction_random), binwidth = 1) +
  theme_classic()
```


#### Plot. Scatterplot of random wind direction vs. observed upwind direction

```{r echo=FALSE}
aqs_daily_annuli_random_wind %>%
  sample_n(100000) %>%
  ggplot(aes(narr_wind_direction, wind_direction_random)) +
  geom_point(alpha = 0.05) +
  geom_smooth(formula = y ~ x, method = "lm", color = "red") +
  theme_classic()
```


#### Model. Observed upwind direction ~ Random wind direction

No association b/t the two

```{r echo=FALSE}
lm(narr_wind_direction ~ wind_direction_random, 
   data = aqs_daily_annuli_random_wind) %>%
  summary()
```


#### Plot. Distribution of random wind direction vector by CARB air basin

```{r echo=FALSE}
aqs_daily_annuli_random_wind %>%
  ggplot() +
  geom_histogram(aes(wind_direction_random), binwidth = 1) +
  theme_classic() +
  facet_wrap(~ carb_basin)
```

#### Plot. Distribution of random wind direction vector by monitor

On a subset of randomly-selected monitors

```{r echo=FALSE, warning=FALSE, message=FALSE}
random_monitors <- aqs_sites %>% sample_n(20) %>% select(monitor_id)
aqs_daily_annuli_random_wind %>%
  filter(monitor_id %in% random_monitors$monitor_id) %>%
  ggplot() +
  geom_histogram(aes(wind_direction_random), binwidth = 1) +
  theme_classic() +
  facet_wrap(~ monitor_id)
```


#### Plot. Scatterplot of random wind direction vs. observed upwind direction by montior

On a subset of randomly-selected monitors, same subset as above

```{r echo=FALSE, warning=FALSE, message=FALSE}
aqs_daily_annuli_random_wind %>%
  filter(monitor_id %in% random_monitors$monitor_id) %>%
  ggplot(aes(narr_wind_direction, wind_direction_random)) +
  geom_point(alpha = 0.05) +
  geom_smooth(formula = y ~ x, method = "lm", color = "red") +
  theme_classic() +
  facet_wrap(~ monitor_id)
```

*Note:* It looks liek we should do a nested randomization by monitor for monitors with few observations

## Summary

