---
title: "Memo - Distribution of exposure by monitor-day"
output: html_notebook
date: "01-27-2021"
---


```{r setup, include=FALSE}
source("../../code/0-setup/1-setup.R")
library("lfe")
```

```{r data_input, include=FALSE}
aqs_sites <- readRDS("../../data/interim/aqs_sites.rds") %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)
aqs_daily_annuli_preproduction <- 
  readRDS("../../data/processed/aqs_daily_annuli_preproduction.rds")
#### add production exposure data
```


## Objectives

This memo explore the distribution of exposure in monitor-days, i.e., the number of monitor-day observations with exposure to > 0 preproduction wells and/or > 0 production volume in each of the the 1-km annuli.


## Visualizations

### Preproduction well count

#### Plot. Monitor-days with exposure to at least one well by annulus, all monitors

```{r echo=FALSE}
data_plot <- tibble(
  distance_km = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
  wind_direction = c("upwind", "upwind", "upwind", "upwind", "upwind",
                     "upwind", "upwind", "upwind", "upwind", "upwind",
                     "downwind", "downwind", "downwind", "downwind", "downwind", 
                     "downwind", "downwind", "downwind", "downwind", "downwind"),
  # count of observations in monitor-days
  n_observations = c(nrow(subset(aqs_daily_annuli_preproduction, # upwind
                                 preprod_count_uw_0to1km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_uw_1to2km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_uw_2to3km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_uw_3to4km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_uw_4to5km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_uw_5to6km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_uw_6to7km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_uw_7to8km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_uw_8to9km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_uw_9to10km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction, # downwind
                                 preprod_count_dw_0to1km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_dw_1to2km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_dw_2to3km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_dw_3to4km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_dw_4to5km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_dw_5to6km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_dw_6to7km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_dw_7to8km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_dw_8to9km > 0)),
                     nrow(subset(aqs_daily_annuli_preproduction,
                                 preprod_count_dw_9to10km > 0)))
)
```

```{r echo=FALSE}
data_plot %>%
  ggplot() +
  geom_bar(aes(distance_km, n_observations), stat = "identity") +
  theme_classic() +
  facet_wrap(. ~ wind_direction)
```

*Note:* Observations are in monitor-days


#### Plot. Sum of preproduction wells observed by annulus, all monitors

```{r echo=FALSE}
data_plot <- tibble(
  distance_km = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
  wind_direction = c("upwind", "upwind", "upwind", "upwind", "upwind",
                     "upwind", "upwind", "upwind", "upwind", "upwind",
                     "downwind", "downwind", "downwind", "downwind", "downwind", 
                     "downwind", "downwind", "downwind", "downwind", "downwind"),
  # count of observations in monitor-days
  total_wells = c(sum(aqs_daily_annuli_preproduction$preprod_count_uw_0to1km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_uw_1to2km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_uw_2to3km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_uw_3to4km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_uw_4to5km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_uw_5to6km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_uw_6to7km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_uw_7to8km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_uw_8to9km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_uw_9to10km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_dw_0to1km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_dw_1to2km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_dw_2to3km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_dw_3to4km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_dw_4to5km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_dw_5to6km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_dw_6to7km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_dw_7to8km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_dw_8to9km),
                  sum(aqs_daily_annuli_preproduction$preprod_count_dw_9to10km))
)
```

```{r echo=FALSE}
data_plot %>%
  ggplot() +
  geom_bar(aes(distance_km, total_wells), stat = "identity") +
  theme_classic() +
  facet_wrap(. ~ wind_direction)
```


### Prodution volume sum

#### Plot. Monitor-days with exposure to at least one BOE by annulus, all monitors

```{r echo=FALSE}
data_plot <- tibble(
  distance_km = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
  wind_direction = c("upwind", "upwind", "upwind", "upwind", "upwind",
                     "upwind", "upwind", "upwind", "upwind", "upwind",
                     "downwind", "downwind", "downwind", "downwind", "downwind", 
                     "downwind", "downwind", "downwind", "downwind", "downwind"),
  # count of observations in monitor-days
  n_observations = c(nrow(subset(aqs_daily_annuli_production, # upwind
                                 prod_volume_upwind_0to1km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_upwind_1to2km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_upwind_2to3km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_upwind_3to4km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_upwind_4to5km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_upwind_5to6km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_upwind_6to7km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_upwind_7to8km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_upwind_8to9km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_upwind_9to10km > 0)),
                     nrow(subset(aqs_daily_annuli_production, # downwind
                                 prod_volume_downwind_0to1km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_downwind_1to2km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_downwind_2to3km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_downwind_3to4km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_downwind_4to5km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_downwind_5to6km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_downwind_6to7km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_downwind_7to8km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_downwind_8to9km > 0)),
                     nrow(subset(aqs_daily_annuli_production,
                                 prod_volume_downwind_9to10km > 0)))
)
```

```{r echo=FALSE}
data_plot %>%
  ggplot() +
  geom_bar(aes(distance_km, n_observations), stat = "identity") +
  theme_classic() +
  facet_wrap(. ~ wind_direction)
```


#### Plot. Total production volume observed by annulus, all monitors

```{r echo=FALSE}
data_plot <- tibble(
  distance_km = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
  wind_direction = c("upwind", "upwind", "upwind", "upwind", "upwind",
                     "upwind", "upwind", "upwind", "upwind", "upwind",
                     "downwind", "downwind", "downwind", "downwind", "downwind", 
                     "downwind", "downwind", "downwind", "downwind", "downwind"),
  # count of observations in monitor-days
  total_production = c(sum(aqs_daily_annuli_production$prod_volume_upwind_0to1km),
                       sum(aqs_daily_annuli_production$prod_volume_upwind_1to2km),
                       sum(aqs_daily_annuli_production$prod_volume_upwind_2to3km),
                       sum(aqs_daily_annuli_production$prod_volume_upwind_3to4km),
                       sum(aqs_daily_annuli_production$prod_volume_upwind_4to5km),
                       sum(aqs_daily_annuli_production$prod_volume_upwind_5to6km),
                       sum(aqs_daily_annuli_production$prod_volume_upwind_6to7km),
                       sum(aqs_daily_annuli_production$prod_volume_upwind_7to8km),
                       sum(aqs_daily_annuli_production$prod_volume_upwind_8to9km),
                       sum(aqs_daily_annuli_production$prod_volume_upwind_9to10km),
                       sum(aqs_daily_annuli_production$prod_volume_downwind_0to1km),
                       sum(aqs_daily_annuli_production$prod_volume_downwind_1to2km),
                       sum(aqs_daily_annuli_production$prod_volume_downwind_2to3km),
                       sum(aqs_daily_annuli_production$prod_volume_downwind_3to4km),
                       sum(aqs_daily_annuli_production$prod_volume_downwind_4to5km),
                       sum(aqs_daily_annuli_production$prod_volume_downwind_5to6km),
                       sum(aqs_daily_annuli_production$prod_volume_downwind_6to7km),
                       sum(aqs_daily_annuli_production$prod_volume_downwind_7to8km),
                       sum(aqs_daily_annuli_production$prod_volume_downwind_8to9km),
                       sum(aqs_daily_annuli_production$prod_volume_downwind_9to10km))
)
```

```{r echo=FALSE}
data_plot %>%
  ggplot() +
  geom_bar(aes(distance_km, total_production), stat = "identity") +
  theme_classic() +
  facet_wrap(. ~ wind_direction)
`````


## Summary