---
title: "Data Exploration: CalGEM Production"
output: html_notebook
---


```{r setup_input_tidy, include=FALSE}
# sets up R environment
source("../../code/0-setup/1-setup.R")

# inputs data
calgem_production_monthly <- 
  readRDS("../../data/interim/calgem_production_monthly.rds")
wells_interim <- readRDS("../../data/interim/wells_interim.rds")

calgem_production_wells_sf <- calgem_production_monthly %>%
  distinct(pwt_id) %>%
  st_as_sf() ##### pick up here, considering making summary statistics grouping by pwt_id
```


## Descriptive statistics

- The dataset includes observations from `r calgem_production_monthly %>% distinct(pwt_id) %>% nrow()` wells, 1999-2017
- `r calgem_production_monthly %>% filter(oil_produced >= 0 | gas_produced >= 0) %>% nrow()` observations include an observation for oil or gas production, and `r  calgem_production_monthly %>% filter(oil_produced > 0 | gas_produced > 0) %>% nrow()` of those had production > 0 barrels

### Missingness

- Of the `r calgem_production_monthly %>% filter(oil_produced > 0 | gas_produced > 0) %>% nrow()` well-months with oil/gas production, in the dataset, **`r calgem_production_monthly %>% filter(oil_produced > 0 | gas_produced > 0) %>% filter(is.na(longitude)) %>% nrow()` (3.1%) are missing lat/long data**
- Volume of oil/gas with missing lat/long data
- This isn't ideal, but I think we're okay to move forward with these data! Particulary for 2001-2013 (see plots below)

#### Plot. Missingness by month, lat/long, all well-months

```{r echo=FALSE, warning=FALSE}
calgem_production_monthly %>%
  filter(is.na(longitude)) %>%
  group_by(prod_month_year) %>%
  summarize(n = n()) %>%
  ggplot() + 
  geom_bar(aes(prod_month_year, n), stat = "identity") +
  theme_classic()
```

#### Plot. Missingness by month, lat/long, well-months with production

```{r echo=FALSE, warning=FALSE}
calgem_production_monthly %>%
  filter(oil_produced > 0 | gas_produced > 0) %>%
  filter(is.na(longitude)) %>%
  group_by(prod_month_year) %>%
  summarize(n = n()) %>%
  ggplot() + 
  geom_bar(aes(prod_month_year, n), stat = "identity") +
  theme_classic()
```

**Most missingness for producing well-months is before 2001 and after 2013; do a sensitivity analysis for 2001-2013**

#### Plot. Volume of oil with mising lat/long, well-months with production

```{r echo=FALSE, warning=FALSE}
calgem_production_monthly %>%
  filter(oil_produced > 0) %>%
  filter(is.na(longitude)) %>%
  group_by(prod_month_year) %>%
  summarize(oil_production = sum(oil_produced)) %>%
  ggplot() + 
  geom_bar(aes(prod_month_year, oil_production), stat = "identity") +
  theme_classic()
```

#### Plot. Volume of oil with mising lat/long by year

```{r echo=FALSE, warning=FALSE}
calgem_production_monthly %>%
  mutate(year = as.factor(year(prod_month_year))) %>%
  filter(oil_produced > 0) %>%
  filter(is.na(longitude)) %>%
  group_by(year) %>%
  summarize(oil_production = sum(oil_produced)) %>%
  ggplot() + 
  geom_bar(aes(year, oil_production), stat = "identity") +
  theme_classic()
```


#### Plot. Volume of gas with mising lat/long, well-months with production

```{r echo=FALSE, warning=FALSE}
calgem_production_monthly %>%
  filter(gas_produced > 0) %>%
  filter(is.na(longitude)) %>%
  group_by(prod_month_year) %>%
  summarize(gas_production = sum(gas_produced)) %>%
  ggplot() + 
  geom_bar(aes(prod_month_year, gas_production), stat = "identity") +
  theme_classic()
```

#### Plot. Volume of gas with mising lat/long by year

```{r echo=FALSE, warning=FALSE}
calgem_production_monthly %>%
  mutate(year = as.factor(year(prod_month_year))) %>%
  filter(gas_produced > 0) %>%
  filter(is.na(longitude)) %>%
  group_by(year) %>%
  summarize(gas_production = sum(gas_produced)) %>%
  ggplot() + 
  geom_bar(aes(year, gas_production), stat = "identity") +
  theme_classic()
```

## Temporal variation

#### Plot. Well count through time

```{r echo=FALSE}
calgem_production_monthly %>% 
  group_by(prod_month_year) %>%
  summarize(observations = n()) %>%
  ggplot() +
  geom_bar(aes(prod_month_year, observations), stat = "identity") +
  theme_classic()
```


#### Plot. Monthly oil production, total, 1999-2019

```{r echo=FALSE}
calgem_production_monthly %>%
  #filter(prod_month_year < as.Date("2001-01-01", format = "%Y-%m-%d")) %>%
  group_by(prod_month_year) %>%
  summarize(sum_oil_produced = sum(oil_produced, na.rm = TRUE)) %>%
  ggplot() +
    geom_line(aes(prod_month_year, sum_oil_produced)) + 
    labs(x = "Time", y = "Sum Oil Produced (barrels)") + 
    theme_classic()
```

#### Plot. Monthly gas production, total, 1999-2019

```{r echo=FALSE}
calgem_production_monthly %>%
  group_by(prod_month_year) %>%
  summarize(sum_gas_produced = sum(gas_produced, na.rm = TRUE)) %>%
  ggplot() +
    geom_line(aes(prod_month_year, sum_gas_produced)) + 
    labs(x = "Time", y = "Sum Gas Produced (BTW)") + 
    theme_classic()
```

#### Plot. Total monthly water production, 1999-2019

```{r echo=FALSE}
calgem_production_monthly %>%
  group_by(prod_month_year) %>%
  summarize(sum_water_produced = sum(water_produced, na.rm = TRUE)) %>%
  ggplot() +
    geom_line(aes(prod_month_year, sum_water_produced)) + 
    labs(x = "Time", y = "Sum Water Produced (units?)") + 
    theme_classic()
```

```{r}

```
