---
title: "Ch. 3: Oil Production and Air Quality in California"
subtitle: "Data Exploration: Air Quality Data"
output: html_notebook
---

```{r setup, include=FALSE}
# loads necessary packages and defines global variables
  source("../../code/0-setup/01-setup.R")
```

```{r data_import, echo=FALSE, include=FALSE}
# imports raw data
  # California Air Resources Board (CARB) - administrative shapefiles
  carb_air_basins_raw <-
    st_read("../../data/raw/cal_epa/carb_air_basins/CaAirBasin.shp")
  carb_air_districts_raw <-
    st_read("../../data/raw/cal_epa/carb_air_districts/CaAirDistrict.shp")
  
  # CalGEM - production, shapefiles
  calgem_fields_raw <- 
    st_read("../../data/raw/cal_gem/field_boundaries/DOGGR_Admin_Boundaries_Master.shp")
  
  # DrillingInfo - oil and gas well sites
  di_wells_raw <-
    read_csv("../../data/raw/drillinginfo/california_wells_jan2019.csv")
  
# US EPA Air Quality System (AQS) - ambient air quality
  aqs_co_raw <- list.files("../../data/raw/us_epa/air_quality_system/co", # gets names
                            pattern = "epa_aqs_co", full.names = T) %>%
    map_df(~read_csv(.))
  
  aqs_no2_raw <- list.files("../../data/raw/us_epa/air_quality_system/no2",
                               pattern = "epa_aqs_no2", full.names = T) %>%
    map_df(~read_csv(.))  # imports all files
  
  aqs_ozone_raw <- list.files("../../data/raw/us_epa/air_quality_system/ozone",
                                 pattern = "epa_aqs_ozone", full.names = T) %>%
    map_df(~read_csv(.))
  
  aqs_pm2.5_raw <- list.files("../../data/raw/us_epa/air_quality_system/pm25",
                                 pattern = "epa_aqs_pm25", full.names = T) %>%
    map_df(~read_csv(.))
  
  aqs_pm10_raw <- list.files("../../data/raw/us_epa/air_quality_system/pm10",
                                pattern = "epa_aqs_pm10", full.names = T) %>%
    map_df(~read_csv(.))
  
  aqs_so2_raw <- list.files("../../data/raw/us_epa/air_quality_system/so2", # gets names
                           pattern = "epa_aqs_so2", full.names = T) %>%
    map_df(~read_csv(.))  # imports all files
```

```{r data_tidying, include=FALSE}
# loads functions for tidying the data
  source("../../code/2-tidying/01-tidy_airnow_data.R")
  #source("../../code/2-tidying/02-tidy_drilling_data.R")

# prepares US EPA Air Quality System (AQS) data
  aqs_co   <- prepAirQualityData(aqs_co_raw, 
                                  "daily_max_co_concentration", 
                                  "Daily Max 8-hour CO Concentration") %>%
    # summarizes mean monthly concentration for each pollutant; it's easier
    # to do this outside the prepAirQualityData function
    group_by(site_id, month_year) %>%
    dplyr::summarize(monthly_mean_co = mean(daily_max_co_concentration,
                                             na.rm = TRUE))

  aqs_no2   <- prepAirQualityData(aqs_no2_raw, 
                                 "daily_max_no2_concentration", 
                                 "Daily Max 1-hour NO2 Concentration") %>%
    # summarizes mean monthly concentration for each pollutant; it's easier
    # to do this outside the prepAirQualityData function
    group_by(site_id, month_year) %>%
    dplyr::summarize(monthly_mean_no2 = mean(daily_max_no2_concentration,
                                             na.rm = TRUE))
  
  aqs_ozone <- prepAirQualityData(aqs_ozone_raw, 
                                 "daily_max_ozone_concentration", 
                                 "Daily Max 8-hour Ozone Concentration") %>%
    # summarizes mean monthly concentration for each pollutant; it's easier
    # to do this outside the prepAirQualityData function
    group_by(site_id, month_year) %>%
    dplyr::summarize(monthly_mean_ozone = mean(daily_max_ozone_concentration,
                                               na.rm = TRUE))
  
  aqs_pm2.5 <- prepAirQualityData(aqs_pm2.5_raw, 
                                 "daily_mean_pm2.5_concentration", 
                                 "Daily Mean PM2.5 Concentration") %>%
    # summarizes mean monthly concentration for each pollutant; it's easier
    # to do this outside the prepAirQualityData function
    group_by(site_id, month_year) %>%
    dplyr::summarize(monthly_mean_pm2.5 = mean(daily_mean_pm2.5_concentration,
                                               na.rm = TRUE))
  
  aqs_pm10  <- prepAirQualityData(aqs_pm10_raw, 
                                 "daily_mean_pm10_concentration", 
                                 "Daily Mean PM10 Concentration") %>%
    # summarizes mean monthly concentration for each pollutant; it's easier
    # to do this outside the prepAirQualityData function
    group_by(site_id, month_year) %>%
    dplyr::summarize(monthly_mean_pm10 = mean(daily_mean_pm10_concentration,
                                              na.rm = TRUE))
  
  aqs_so2   <- prepAirQualityData(aqs_so2_raw, 
                                  "daily_max_so2_concentration", 
                                  "Daily Max 1-hour SO2 Concentration") %>%
    # summarizes mean monthly concentration for each pollutant; it's easier
    # to do this outside the prepAirQualityData function
    group_by(site_id, month_year) %>%
    dplyr::summarize(monthly_mean_so2 = mean(daily_max_so2_concentration,
                                             na.rm = TRUE))
  
  # merges pollutant observations across all 'aqs_sites' to make one
  # combined tibble with all observations
  
    # for each pollutant, creates unique id for each 'site_id_month_year'; 
    # then uses 'aqs_no2' as the base tibble, strips redundant variables from
    # the tibbles for the other three pollutants, and calls a left_join
    aqs_ozone <- aqs_ozone %>%
      # creates unique id for each site_id_month_year
      mutate(site_id_month_year = paste(site_id, month_year, sep = "-"))
    aqs_ozone$site_id_month_year <- 
      as.factor(aqs_ozone$site_id_month_year)
    
    aqs_co <- aqs_co %>%
      mutate(site_id_month_year = paste(site_id, month_year, sep = "-")) %>%
      dplyr::select(site_id_month_year, site_id, monthly_mean_co)
    
    aqs_no2 <- aqs_no2 %>%
      mutate(site_id_month_year = paste(site_id, month_year, sep = "-")) %>%
      dplyr::select(site_id_month_year, site_id, monthly_mean_no2)
    
    aqs_pm10 <- aqs_pm10 %>%
      mutate(site_id_month_year = paste(site_id, month_year, sep = "-")) %>%
      dplyr::select(site_id_month_year, site_id, monthly_mean_pm10)
    
    aqs_pm2.5 <- aqs_pm2.5 %>%
      mutate(site_id_month_year = paste(site_id, month_year, sep = "-")) %>%
      dplyr::select(site_id_month_year, site_id, monthly_mean_pm2.5)
    
    aqs_so2 <- aqs_so2 %>%
      mutate(site_id_month_year = paste(site_id, month_year, sep = "-")) %>%
      dplyr::select(site_id_month_year, site_id, monthly_mean_so2)
    
    # makes final combined dataset
    aqs_combined <- 
      left_join(aqs_ozone, aqs_co, by = "site_id_month_year") %>%
      left_join(aqs_no2, by = "site_id_month_year") %>%
      left_join(aqs_pm10, by = "site_id_month_year") %>%
      left_join(aqs_pm2.5, by = "site_id_month_year") %>%
      left_join(aqs_so2, by = "site_id_month_year") %>%
      # cleans up and arranges columns
      mutate(site_id = site_id.x) %>%
      dplyr::select(site_id, 
                    month_year, 
                    site_id_month_year, 
                    monthly_mean_co,
                    monthly_mean_ozone,
                    monthly_mean_no2, 
                    monthly_mean_pm10, 
                    monthly_mean_pm2.5, 
                    monthly_mean_so2)#, 
                    #site_id.x)
    
    # converts 'site_id_month_year' to factor
    aqs_combined$site_id_month_year <- 
      as.factor(aqs_combined$site_id_month_year)
    
    # gets lat/long data from raw data and joins by site_id
    aqs_lat_long <- aqs_ozone_raw %>%
      mutate(site_id   = as.factor(`Site ID`),
             latitude  = SITE_LATITUDE,
             longitude = SITE_LONGITUDE) %>%
      dplyr::select(site_id, longitude, latitude) %>%
      distinct()
    
    # makes final 'aqs_combined' dataset before analysis
    aqs_combined <- aqs_combined %>%
      # joins lat/long data to combined airnow dataset
      left_join(aqs_lat_long, by = "site_id") %>%
      # adds column to capture inverse distance weighted (IDW) index
      # in the exposure assessment below
      mutate(idw_index = NA)
```

```{r data_tidying2, include=FALSE}
# prepares datasets necessary for this notebook

  # sites of air quality monitors, sf object
  aqs_sites <- aqs_combined %>%
    distinct(site_id, .keep_all = TRUE) %>%
    st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

  # preps CalGEM fields data; needs to happen before prepDrillingData()
    calgem_fields <- calgem_fields_raw %>%
      st_transform(crs_nad83) %>%
      # renames varible names
      mutate(field_object_id    = OBJECTID,  # not sure what this is
             field_name         = NAME,
             field_code         = FIELD_CODE,
             field_area_sq_mile = AREA_SQ_MI,
             field_area_acre    = AREA_ACRE,
             field_perimeter    = PERIMETER,
             field_start_date   = StartDate,
             field_end_date     = EndDate,
             district_name      = District) %>%
      # keeps only the variables we need
      select(field_object_id:district_name)

  # preps DrillingInfo wells data
  di_wells <- prepDrillingData(di_wells_raw)
    
  # wells in preproduction stage during the study period, sf object
  wells_preprod <- di_wells %>%
    filter(drilled_1999_to_2019 == 1) %>%
    st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)
    
  # wells in production stage during the study period, sf object
  wells_prod <- di_wells %>%
    filter(prod_1999_to_2019 == 1) %>%
    st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)
  
  # makes 5 km buffer around well sites in preproduction stage
  wells_preprod_buffer <- wells_preprod %>%
    # transforms objected to projected CRS, necessary before making buffer
    st_transform(crs_projected) %>%
    # makes 5,000 m buffer
    st_buffer(dist = 5000) %>%  # distance in meters
    # merges overlapping polygons
    st_union() 
  
  # makes 5 km buffer around well sites in production stage
  wells_prod_buffer <- wells_prod %>%
    # transforms objected to projected CRS, necessary before making buffer
    st_transform(crs_projected) %>%
    # makes 5,000 m buffer
    st_buffer(dist = 5000) %>%  # distance in meters
    # merges overlapping polygons
    st_union() 
```

### Overview

This Rmarkdown notebook explores exposure data for Ch. 3 of my dissertation project. This study uses air quality and drilling from 1999 to 2019 across California.

#### Data sources

- California Air Resources Board - administrative shapefiles
- Enverus (formerly DrillingInfo) - well sites
- US EPA Air Quality System (AQS) - monitoring sites, air pollutant concentrations
- US Census Bureau - administrative shapefiles

For this project, we used data from **`r length(levels(aqs_combined$site_id))`** unique monitors from the AQS dataset. We obtained data on concentrations of four air pollutants from 1999 to 2019: CO, O3, NO2, PM10, PM2.5, and SO2. Note that not all monitors monitor all pollutants.

### Air Quality Monitors

#### Map. Location of air quality monitors and oil fields

```{r echo=FALSE}
# makes map
ggplot() +
  geom_sf(data = st_union(cal_counties), fill = "#FFFFFF") +
  geom_sf(data = calgem_fields, color = "red") +
  geom_sf(data = aqs_sites, shape = 1) +
  theme_bw()
```




#### Map. Location of air quality monitors and air basins

```{r echo=FALSE}
# makes map
ggplot() +
  geom_sf(data = carb_air_basins, 
          aes(fill = NAME), color = "#FFFFFF", alpha = 0.7) +
  geom_sf(data = aqs_sites, shape = 1) +
  theme_bw()
```


We used data on **`r di_wells %>% filter(drilled_1999_to_2019 == 1) %>% nrow()`** well sites in preproduction and **`r di_wells %>% filter(prod_1999_to_2019 == 1) %>% nrow()`** well sites in production in California during the study period (1999-2019). Note that these groups are not mutually exclusive. Well sites were most highly concentrated in the Central Valley and Southern California. 

#### Map. Location of air quality monitors and well sites

The orange shaded area is a 5 km buffer around well sites in preproduction stage. The dark gray shaded area is a 5 km buffer around well sites in the production stage.

```{r echo=FALSE}
ggplot() +
  geom_sf(data = cal_counties, fill = "#000000", color = NA, alpha = 0.2) +
  geom_sf(data = wells_prod_buffer, fill = "#000000", alpha = 0.7) +
  geom_sf(data = wells_preprod_buffer, fill = "#f1a340", alpha = 0.7) +
  geom_sf(data = aqs_sites, shape = 2, alpha = 0.7) +
  theme_bw()
```


### Distribution of Pollutant Concentrations

///// organize by pollutant? map monitors by pollutant?

#### Distribution of CO Concentrations

```{r echo=FALSE, warning=FALSE}
aqs_combined %>%
  ggplot() +
    geom_histogram(aes(monthly_mean_co), bins = 100) + 
    labs(x = "Mean Monthly CO Concentration (ppm)", y = "Count") + 
    theme_classic()
```

#### Distribution of N02 Concentrations

```{r echo=FALSE, warning=FALSE}
aqs_combined %>%
  ggplot() +
    geom_histogram(aes(monthly_mean_no2), bins = 100) + 
    labs(x = "Mean Monthly NO2 Concentration (ppb)", y = "Count") + 
    theme_classic()
```

#### Distribution of Ozone Concentrations

```{r echo=FALSE, warning=FALSE}
aqs_combined %>%
  ggplot() +
    geom_histogram(aes(monthly_mean_ozone), bins = 100) + 
    labs(x = "Mean Monthly Ozone Concentration (ppm)", y = "Count") + 
    theme_classic()
```

#### Distribution of PM10 Concentrations

This distibution is right-skewed

```{r echo=FALSE, warning=FALSE}
aqs_combined %>%
  ggplot() +
    geom_histogram(aes(monthly_mean_pm10), bins = 100) + 
    labs(x = "Mean Monthly PM10 Concentration (µg/m^3)", y = "Count") + 
    theme_classic()
```

#### Distribution of PM2.5 Concentrations

```{r echo=FALSE, warning=FALSE}
aqs_combined %>%
  ggplot() +
    geom_histogram(aes(monthly_mean_pm2.5), bins = 100) + 
    labs(x = "Mean Monthly PM2.5 Concentration (µg/m^3)", y = "Count") + 
    theme_classic()
```

#### Distribution of SO2 Concentrations

```{r echo=FALSE, warning=FALSE}
aqs_combined %>%
  ggplot() +
    geom_histogram(aes(monthly_mean_so2), bins = 100) + 
    labs(x = "Mean Monthly SO2 Concentration (ppb)", y = "Count") + 
    theme_classic()
```

### Pollutant Concentrations by Month

#### CO Concentration by Month

```{r echo=FALSE, warning=FALSE}
aqs_combined %>%
  ggplot() +
    geom_point(aes(month_year, monthly_mean_co), alpha = 0.2) + 
    labs(x = "Time", y = "Mean Monthly CO Concentration (ppm)") + 
    theme_classic()
```

#### NO2 Concentration by Month

```{r echo=FALSE, warning=FALSE}
aqs_combined %>%
  ggplot() +
    geom_point(aes(month_year, monthly_mean_no2), alpha = 0.2) + 
    labs(x = "Time", y = "Mean Monthly NO2 Concentration (ppb)") + 
    theme_classic()
```

#### Ozone Concentration by Month

```{r echo=FALSE, warning=FALSE}
aqs_combined %>%
  ggplot() +
    geom_point(aes(month_year, monthly_mean_ozone), alpha = 0.2) + 
    labs(x = "Time", y = "Mean Monthly Ozone Concentration (ppm)") + 
    theme_classic()
```

#### PM10 Concentration by Month

```{r echo=FALSE, warning=FALSE}
aqs_combined %>%
  ggplot() +
    geom_point(aes(month_year, monthly_mean_pm10), alpha = 0.2) + 
    labs(x = "Time", y = "Mean Monthly PM10 Concentration (µg/m^3)") + 
    theme_classic()
```

#### PM2.5 Concentration by Month

```{r echo=FALSE, warning=FALSE}
aqs_combined %>%
  ggplot() +
    geom_point(aes(month_year, monthly_mean_pm2.5), alpha = 0.2) + 
    labs(x = "Time", y = "Mean Monthly PM2.5 Concentration (µg/m^3)") + 
    theme_classic()
```

#### SO2 Concentration by Month

```{r echo=FALSE, warning=FALSE}
aqs_combined %>%
  ggplot() +
    geom_point(aes(month_year, monthly_mean_so2), alpha = 0.2) + 
    labs(x = "Time", y = "Mean Monthly SO2 Concentration (ppb)") + 
    theme_classic()
```



### Concentrations by Air Basin

```{r echo=FALSE, include=FALSE}
##### move to data prep
aqs_combined_sf <- aqs_combined %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  st_join(carb_air_basins)
  
##### makes figure
aqs_combined_sf %>%
  ggplot() +
    geom_smooth(aes(month_year, monthly_mean_pm2.5), alpha = 0.2) + 
    labs(x = "Time", y = "Mean Monthly PM2.5 Concentration (µg/m^3)") + 
    facet_wrap(~ NAME) +
    theme_classic()
```

