---
title: "Ch. 3: Oil Production and Air Quality in California"
subtitle: "Data Exploration: Exposure with 1-km annuli"
output: html_notebook
---

```{r setup, include=FALSE}
# sets up RStudio workspace
  source("../../code/0-setup/01-setup.R")
```

```{r data_import, include=FALSE}
# imports raw data
  # California Air Resources Board (CARB) - administrative shapefiles
  carb_air_basins_raw <-
    st_read("../../data/raw/cal_epa/carb_air_basins/CaAirBasin.shp")
  carb_air_districts_raw <-
    st_read("../../data/raw/cal_epa/carb_air_districts/CaAirDistrict.shp")
  # DrillingInfo - oil and gas well sites
  di_wells_raw <-
    read_csv("../../data/raw/drillinginfo/california_wells_jan2019.csv")
  # US Census Bureau - administrative shapefiles
  cal_counties_raw <- 
    st_read("../../data/raw/us_census/admin_shp/cal_counties.shp")
  us_states_raw <- 
    st_read("../../data/raw/us_census/admin_shp/tl_2018_us_state.shp")
  
# imports interim data
  aqs_exposure_annuli <- read_csv("../../data/interim/aqs_exposure_annuli.csv")
```

```{r data_tidying, include=FALSE}
# loads functions for tidying the data
  source("../../code/2-tidying/02-tidy_drilling_data.R")
    
# calls functions to tidy all necessary datasets
  di_wells <- prepDrillingData(di_wells_raw)

# prepares datasets necessary for this notebook
  
  # California Air Resources Board
  carb_air_basins <- carb_air_basins_raw %>%
    st_transform(crs_nad83)
  carb_air_districts <- carb_air_districts_raw %>%
    st_transform(crs_nad83)
  
  # US Census
  cal_counties <- cal_counties_raw %>%
    st_transform(crs_nad83)
  us_states <- us_states_raw %>%
    st_transform(crs_nad83)    

  # sites of air quality monitors, sf object
  aqs_sites <- aqs_exposure_annuli %>%
    # keeps only each unique air monitor
    distinct(site_id, .keep_all = TRUE) %>% 
    # drops columns we don't need
    select(-c(monthly_mean_co:monthly_mean_so2)) %>%
    # converts to sf object
    st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

  # wells in preproduction stage during the study period, sf object
  wells_preprod <- di_wells %>%
    filter(drilled_1999_to_2019 == 1) %>%
    st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)
    
  # wells in production stage during the study period, sf object
  wells_prod <- di_wells %>%
    filter(prod_1999_to_2019 == 1) %>%
    st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)
  
# preps wells data for making maps
  # makes dataset with wells
  wells_sf <- di_wells %>%
    st_as_sf(crs = crs_nad83, coords = c("longitude", "latitude"))
  
# subsets wells data into two mutually exclusive datasets: well sites in 
# (a) preproduction and (b) production stages
  # well sites in production
  wells_sf_preprod <- wells_sf %>%
    filter(drilled_1999_to_2019 == 1)
  # well sites in preproduction
  wells_sf_prod <- wells_sf %>%
    filter(drilled_1999_to_2019 == 0 & prod_1999_to_2019 == 1)
  
  # preps data for FE models
  aqs_exposure_annuli <- aqs_sites %>%
    # spatial join
    st_join(carb_air_basins) %>%
    # drops extraneous columns
    select(-c(wells_preprod_0to1km:wells_prod_14to15km), - month_year) %>%
    # joins with primary dataset
    left_join(aqs_exposure_annuli, by = "site_id") %>%
    # renames necessary variables
    rename(basin_name = NAME)
```

### Overview

This Rmarkdown notebook explores exposure data for Ch. 3 of my dissertation project. This study uses air quality and drilling from 1999 to 2019 across California.

#### Data sources

- California Air Resources Board - administrative shapefiles
- Enverus (formerly DrillingInfo) - well sites
- US EPA Air Quality System (AQS) - monitoring sites, air pollutant concentrations
- US Census Bureau - administrative shapefiles

### Air Quality Monitors and Well Sites

For this study, we used data from **`r nrow(aqs_sites)`** unique monitors from the AQS dataset. We obtained data on concentrations of **six air pollutants from 1999 to 2019: CO, O3, NO2, PM10, PM2.5, and SO2**. Note that not all monitors monitor all pollutants.

We also used data on **`r di_wells %>% filter(drilled_1999_to_2019 == 1) %>% nrow()`** well sites in preproduction and **`r di_wells %>% filter(prod_1999_to_2019 == 1) %>% nrow()`** well sites in production in California during the study period (1999-2019). Note that these groups are not mutually exclusive. Well sites were most highly concentrated in the Central Valley and Southern California.

The orange shaded area is a 5 km buffer around well sites in preproduction stage. The dark gray shaded area is a 5 km buffer around well sites in the production stage.

```{r}
aqs_exposure_annuli %>% 
  group_by(site_id) %>% 
  summarize(idw_sum = sum(idw_index)) %>% 
  filter(annuli_sum_preprod > 0) %>% nrow()
```

## Visualizing Exposure




## Header


```{r echo=FALSE}
ggplot() +
  geom_sf(data = cal_counties, fill = "#000000", color = NA, alpha = 0.2) +
  geom_sf(data = wells_prod_buffer, fill = "#000000", alpha = 0.7) +
  geom_sf(data = wells_preprod_buffer, fill = "#f1a340", alpha = 0.7) +
  geom_sf(data = aqs_sites, shape = 2, alpha = 0.7) +
  theme_bw()
```

**Table. AQS monitors by mean monthly exposure to well sites in preproduction throughout the study period. Arranged in descending order.**

```{r echo=FALSE}
aqs_exposure_annuli %>% 
  group_by(site_id) %>% 
  summarize(annuli_sum = mean(idw_index)) %>%
  mutate(idw_mean = round(idw_mean, digits = 1)) %>%
  arrange(-idw_mean)
```

**Table. AQS monitors by mean monthly exposure to well sites in production throughout the study period. Arranged in descending order.**

```{r echo=FALSE}
aqs_exposure_annuli %>% 
  group_by(site_id) %>% 
  summarize(idw_mean = mean(idw_index)) %>%
  mutate(idw_mean = round(idw_mean, digits = 1)) %>%
  arrange(-idw_mean)
```

More monitors were exposed to well sites in the production stage, and the exposure indices were substantially higher for monitors exposed to producing wells. This is likely due to the high density of producing wells and duration of production.

## Well Sites in Preproduction

The following plots explore data related to exposure of U.S. EPA AirNow monitoring sites to oil and gas drilling sites, 1999-2015.
