---
title: "Data Exploration: AQS HAPS"
output: html_notebook
---

```{r setup_input_tidy, include=FALSE, warning=FALSE, message=FALSE}
# sets up R environment
source("../../code/0-setup/1-setup.R")

# inputs data
aqs_haps_1999_2019 <- 
  readRDS("../../data/raw/us_epa/air_quality_system/haps/aqs_haps_1999_2019.rds")
carb_basin <- 
  st_read("../../data/raw/cal_epa/carb_air_basins/CaAirBasin.shp") %>%
  st_transform(crs_nad83)
wells_interim <- readRDS("../../data/interim/wells_interim.rds")

# tidies data
aqs_haps_sites <- aqs_haps_1999_2019 %>%
  distinct(`Site Num`, .keep_all = TRUE) %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = crs_nad83)
wells_buffer_drilling_10km <- wells_interim %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  filter(preprod_1999_to_2019 == 1) %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)
wells_buffer_drilling_1km <- wells_interim %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  filter(preprod_1999_to_2019 == 1) %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
wells_buffer_production_10km <- wells_interim %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  filter(prod_1999_to_2019 == 1) %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)
wells_buffer_production_1km <- wells_interim %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  filter(prod_1999_to_2019 == 1) %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
sites_near_drilling <- aqs_haps_sites %>% 
  st_intersection(wells_buffer_drilling_10km)
sites_near_production <- aqs_haps_sites %>% 
  st_intersection(wells_buffer_production_10km)
```

## Spatial and Temporal Variation

- n = `r aqs_haps_sites %>% nrow()` AQS sites monitor for hazardous air pollutants (HAPs).
- n = `r aqs_haps_sites %>% st_intersection(wells_buffer_drilling_10km) %>% nrow()` HAPs monitoring sites within 10 km of at least one drilling site, and n = `r aqs_haps_sites %>% st_intersection(wells_buffer_drilling_1km) %>% nrow()` are within 1 km
- n = `r aqs_haps_sites %>% st_intersection(wells_buffer_production_10km) %>% nrow()` HAPs monitoring sites within 10 km of at least one drilling site, and n = `r aqs_haps_sites %>% st_intersection(wells_buffer_production_1km) %>% nrow()` are within 1 km

#### Plot. Map of HAPs monitoring sites and well buffers

```{r echo=FALSE}
ggplot() +
  geom_sf(data = carb_basin, fill = "white", color = "lightgray") +
  geom_sf(data = wells_buffer_production_10km, 
          fill = "gold3", color = NA, alpha = 0.2) + 
  geom_sf(data = wells_buffer_production_1km,  
          fill = "gold3", color = NA, alpha = 0.5) + 
  geom_sf(data = wells_buffer_drilling_10km, 
          fill = "purple3", color = NA, alpha = 0.2) + 
  geom_sf(data = wells_buffer_drilling_1km,  
          fill = "purple3", color = NA, alpha = 0.5) + 
  geom_sf(data = aqs_haps_sites, shape = 2) +
  xlim(-124.6, -114.0) + ylim(32.5, 42.1) +
  theme_bw()
```


#### Plot. N observations (monitor-day) observations by year

```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  mutate(Year = as.factor(year(`Date Local`))) %>%
  group_by(Year) %>%
  summarize(n = n()) %>%
  ggplot() +
  geom_bar(aes(Year, n), stat = "identity") +
  theme_classic()
```

#### Plot. N observations (monitor-day) observations by month, 1999-2019

```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  mutate(Month = as.factor(month(`Date Local`))) %>%
  group_by(Month) %>%
  summarize(n = n()) %>%
  ggplot() +
  geom_bar(aes(Month, n), stat = "identity") +
  theme_classic()
```

#### Plot. N observations (monitor-day) observations by month-year

```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  mutate(Month_Year = as.Date(paste(month(`Date Local`), "01", year(`Date Local`),
                                    sep = "/"),
                              format = "%m/%d/%Y")) %>%
  group_by(Month_Year) %>%
  summarize(n = n()) %>%
  ggplot() +
  geom_bar(aes(Month_Year, n), stat = "identity") +
  theme_classic()
```


#### Plot. N observations (monitor-day) observations by monitor

```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  group_by(`Site Num`) %>%
  summarize(n = n()) %>%
  ggplot() +
  geom_bar(aes(reorder(`Site Num`, n), n), stat = "identity") +
  theme_classic() +
  coord_flip()
```

## Pollutant Types

#### N observations (monitor-day) by pollutant type

```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  group_by(`Parameter Name`) %>%
  summarize(n = n())
```

#### Plot. N observations (monitor-day) by pollutant type

```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  group_by(`Parameter Name`) %>%
  summarize(n = n()) %>%
  ggplot() +
  geom_bar(aes(reorder(`Parameter Name`, n), n), stat = "identity") +
  theme_classic() +
  coord_flip()
```


## Potential Exposure

### Monitors near drilling

#### Plot. N observations (monitor-day) observations by month-year near drilling

```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  filter(`Site Num` %in% sites_near_drilling$`Site Num`) %>%
  mutate(Month_Year = as.Date(paste(month(`Date Local`), "01", year(`Date Local`),
                                    sep = "/"),
                              format = "%m/%d/%Y")) %>%
  group_by(Month_Year) %>%
  summarize(n = n()) %>%
  ggplot() +
  geom_bar(aes(Month_Year, n), stat = "identity") +
  theme_classic()
```

#### Plot. N observations (monitor-day) observations by monitor

```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  filter(`Site Num` %in% sites_near_drilling$`Site Num`) %>%
  group_by(`Site Num`) %>%
  summarize(n = n()) %>%
  ggplot() +
  geom_bar(aes(reorder(`Site Num`, n), n), stat = "identity") +
  theme_classic() +
  coord_flip()
```

#### Plot. N observations (monitor-day) by pollutant type near drilling

```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  filter(`Site Num` %in% sites_near_drilling$`Site Num`) %>%
  group_by(`Parameter Name`) %>%
  summarize(n = n()) %>%
  ggplot() +
  geom_bar(aes(reorder(`Parameter Name`, n), n), stat = "identity") +
  theme_classic() +
  coord_flip()
```

This suggests we'll have enough observations for relevant HAPs (e.g., benzyne, formaldehyde) near drilling.

### Monitors near production

#### Plot. N observations (monitor-day) observations by month-year near production

```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  filter(`Site Num` %in% sites_near_production$`Site Num`) %>%
  mutate(Month_Year = as.Date(paste(month(`Date Local`), "01", year(`Date Local`),
                                    sep = "/"),
                              format = "%m/%d/%Y")) %>%
  group_by(Month_Year) %>%
  summarize(n = n()) %>%
  ggplot() +
  geom_bar(aes(Month_Year, n), stat = "identity") +
  theme_classic()
```

#### Plot. N observations (monitor-day) observations by monitor

```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  filter(`Site Num` %in% sites_near_production$`Site Num`) %>%
  group_by(`Site Num`) %>%
  summarize(n = n())
```


```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  filter(`Site Num` %in% sites_near_production$`Site Num`) %>%
  group_by(`Site Num`) %>%
  summarize(n = n()) %>%
  ggplot() +
  geom_bar(aes(reorder(`Site Num`, n), n), stat = "identity") +
  theme_classic() +
  coord_flip()
```

#### Plot. N observations (monitor-day) by pollutant type near production

```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  filter(`Site Num` %in% sites_near_production$`Site Num`) %>%
  group_by(`Parameter Name`) %>%
  summarize(n = n())
```


```{r echo=FALSE}
aqs_haps_1999_2019 %>%
  filter(`Site Num` %in% sites_near_production$`Site Num`) %>%
  group_by(`Parameter Name`) %>%
  summarize(n = n()) %>%
  ggplot() +
  geom_bar(aes(reorder(`Parameter Name`, n), n), stat = "identity") +
  theme_classic() +
  coord_flip()
```

This suggests we'll also have enough observations for relevant HAPs (e.g., benzyne, formaldehyde) near production.