---
title: "Output - Table S1"
output: html_notebook
---

```{r setup, include=FALSE}
source("../../code/0-setup/1-setup.R")
library("table1")
```

```{r data_input, include=FALSE}
aqs_sites <- readRDS("../../data/interim/aqs_sites.rds") %>%
  st_as_sf()
cal_urban <- readRDS("../../data/interim/cal_urban.rds")
carb_basins <- 
  st_read("../../data/raw/cal_epa/carb_air_basins/CaAirBasin.shp") %>%
  st_transform(crs_nad83)
calgem_production <-
  readRDS("../../data/interim/calgem_production_monthly.rds") %>%
  mutate(latlong_id = as.factor(paste(longitude, latitude, sep = "-")))
wells_interim <- readRDS("../../data/interim/wells_interim.rds")
```

```{r, include=FALSE}
aqs_sites_buffer_10km <- aqs_sites %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%  # makes 10 km buffer
  st_union() %>%  # merges overlapping polygons
  st_transform(crs_nad83)  # converts back to unprojected NAD83 CRS for plotting
```

```{r, include=FALSE}
wells_prod <- calgem_production %>% 
  drop_na(longitude) %>%
  filter(prod_month_year >= as.Date("2006-01-01")) %>%
  filter(total_oil_gas_produced > 0) %>%
  distinct(longitude, latitude, .keep_all = TRUE) %>%
  mutate(latlong_id = as.factor(paste(longitude, latitude, sep = "-"))) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)
wells_preprod <- wells_interim %>% 
  filter(preprod_2006_to_2019 == 1) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)
```


### Preproduction well count

**n wells near monitors**

```{r echo=FALSE}
d <- wells_preprod %>%
  st_intersection(aqs_sites_buffer_10km) %>%
  nrow()
d
round(((d / nrow(wells_preprod)) * 100), digits = 1)
```

**n wells in urban areas**

```{r echo=FALSE}
d <- wells_preprod %>%
  st_intersection(st_union(cal_urban)) %>%
  nrow()
d
round(((d / nrow(wells_preprod)) * 100), digits = 1)
```

**n wells by air basins**

Sacramento Valley

```{r echo=FALSE, message=FALSE, warning=FALSE}
basin <- carb_basins %>%
  as_tibble() %>%
  filter(NAME == "Sacramento Valley") %>%
  st_as_sf()
d <- wells_preprod %>%
  st_intersection(basin) %>%
  nrow()
d
round(((d / nrow(wells_preprod)) * 100), digits = 1)
```

San Joaquin Valley

```{r echo=FALSE, message=FALSE, warning=FALSE}
basin <- carb_basins %>%
  as_tibble() %>%
  filter(NAME == "San Joaquin Valley") %>%
  st_as_sf()
d <- wells_preprod %>%
  st_intersection(basin) %>%
  nrow()
d
round(((d / nrow(wells_preprod)) * 100), digits = 1)
```

South Central Coast

```{r echo=FALSE, message=FALSE, warning=FALSE}
basin <- carb_basins %>%
  as_tibble() %>%
  filter(NAME == "South Central Coast") %>%
  st_as_sf()
d <- wells_preprod %>%
  st_intersection(basin) %>%
  nrow()
d
round(((d / nrow(wells_preprod)) * 100), digits = 1)
```

South Coast

```{r echo=FALSE, message=FALSE, warning=FALSE}
basin <- carb_basins %>%
  as_tibble() %>%
  filter(NAME == "South Coast") %>%
  st_as_sf()
d <- wells_preprod %>%
  st_intersection(basin) %>%
  nrow()
d
round(((d / nrow(wells_preprod)) * 100), digits = 1)
```

**n wells by time**

2006-2009

```{r echo=FALSE}
int_2006_2009 <- interval(ymd(20060101), ymd(20091231))
d <- wells_preprod %>%
  mutate(overlaps = 
           case_when(int_overlaps(int_2006_2009, preprod_exp_interval1) ~ 1,
                     int_overlaps(int_2006_2009, preprod_exp_interval1) ~ 1)) %>%
  filter(overlaps == 1) %>%
  nrow()
d
round(((d / nrow(wells_preprod)) * 100), digits = 1)
```

2010-2014

```{r echo=FALSE}
int_2006_2009 <- interval(ymd(20100101), ymd(20141231))
d <- wells_preprod %>%
  mutate(overlaps = 
           case_when(int_overlaps(int_2006_2009, preprod_exp_interval1) ~ 1,
                     int_overlaps(int_2006_2009, preprod_exp_interval1) ~ 1)) %>%
  filter(overlaps == 1) %>%
  nrow()
d
round(((d / nrow(wells_preprod)) * 100), digits = 1)
```

2015-2019

```{r echo=FALSE}
int_2006_2009 <- interval(ymd(20150101), ymd(20191231))
d <- wells_preprod %>%
  mutate(overlaps = 
           case_when(int_overlaps(int_2006_2009, preprod_exp_interval1) ~ 1,
                     int_overlaps(int_2006_2009, preprod_exp_interval1) ~ 1)) %>%
  filter(overlaps == 1) %>%
  nrow()
d
round(((d / nrow(wells_preprod)) * 100), digits = 1)
```

### Production wells

**n wells near monitors**

```{r echo=FALSE}
d <- wells_prod %>%
  st_intersection(aqs_sites_buffer_10km) %>%
  nrow()
d
round(((d / nrow(wells_prod)) * 100), digits = 1)
```

**n wells in urban areas**

```{r echo=FALSE, message=FALSE, warning=FALSE}
d <- wells_prod %>%
  st_intersection(st_union(cal_urban)) %>%
  nrow()
d
round(((d / nrow(wells_prod)) * 100), digits = 1)
```

**n wells by air basins**

Sacramento Valley

```{r echo=FALSE, message=FALSE, warning=FALSE}
basin <- carb_basins %>%
  as_tibble() %>%
  filter(NAME == "Sacramento Valley") %>%
  st_as_sf()
d <- wells_prod %>%
  st_intersection(basin) %>%
  nrow()
d
round(((d / nrow(wells_prod)) * 100), digits = 1)
```

San Joaquin Valley

```{r echo=FALSE, message=FALSE, warning=FALSE}
basin <- carb_basins %>%
  as_tibble() %>%
  filter(NAME == "San Joaquin Valley") %>%
  st_as_sf()
d <- wells_prod %>%
  st_intersection(basin) %>%
  nrow()
d
round(((d / nrow(wells_prod)) * 100), digits = 1)
```

South Central Coast

```{r echo=FALSE, message=FALSE, warning=FALSE}
basin <- carb_basins %>%
  as_tibble() %>%
  filter(NAME == "South Central Coast") %>%
  st_as_sf()
d <- wells_prod %>%
  st_intersection(basin) %>%
  nrow()
d
round(((d / nrow(wells_prod)) * 100), digits = 1)
```

South Coast

```{r echo=FALSE, message=FALSE, warning=FALSE}
basin <- carb_basins %>%
  as_tibble() %>%
  filter(NAME == "South Coast") %>%
  st_as_sf()
d <- wells_prod %>%
  st_intersection(basin) %>%
  nrow()
d
round(((d / nrow(wells_prod)) * 100), digits = 1)
```

**n wells by time**

2006-2009

```{r echo=FALSE}
d <- calgem_production %>%
  filter(total_oil_gas_produced > 0) %>%
  filter(prod_month_year >= as.Date("2006-01-01") &
           prod_month_year <= as.Date("2009-12-31")) %>%
  distinct(longitude, latitude) %>%
  nrow()
d
round(((d / nrow(wells_prod)) * 100), digits = 1)
```

2010-2014

```{r echo=FALSE}
d <- calgem_production %>%
  filter(total_oil_gas_produced > 0) %>%
  filter(prod_month_year >= as.Date("2010-01-01") &
           prod_month_year <= as.Date("2014-12-31")) %>%
  distinct(longitude, latitude) %>%
  nrow()
d
round(((d / nrow(wells_prod)) * 100), digits = 1)
```

2015-2019

```{r echo=FALSE}
d <- calgem_production %>%
  filter(total_oil_gas_produced > 0) %>%
  filter(prod_month_year >= as.Date("2015-01-01") &
           prod_month_year <= as.Date("2019-12-31")) %>%
  distinct(longitude, latitude) %>%
  nrow()
d
round(((d / nrow(wells_prod)) * 100), digits = 1)
```


### Production volume

**sum of volume near monitors**

```{r echo=FALSE}
t <- 3751850237
w <- wells_prod %>%
  st_intersection(aqs_sites_buffer_10km)
p <- calgem_production %>% 
  filter(latlong_id %in% w$latlong_id)
d <- sum(p$total_oil_gas_produced)
d
round(((d / t ) * 100), digits = 1)
```

**n wells in urban areas**

```{r echo=FALSE, message=FALSE, warning=FALSE}
w <- wells_prod %>%
  st_intersection(st_union(cal_urban))
p <- calgem_production %>% 
  filter(prod_month_year >= as.Date("2006-01-01")) %>%
  filter(latlong_id %in% w$latlong_id)
d <- sum(p$total_oil_gas_produced)
d
round(((d / t ) * 100), digits = 1)
```

**n wells by air basins**

Sacramento Valley

```{r echo=FALSE, message=FALSE, warning=FALSE}
basin <- carb_basins %>%
  as_tibble() %>%
  filter(NAME == "Sacramento Valley") %>%
  st_as_sf()
w <- wells_prod %>%
  st_intersection(basin)
p <- calgem_production %>% 
  filter(prod_month_year >= as.Date("2006-01-01")) %>%
  filter(latlong_id %in% w$latlong_id)
d <- sum(p$total_oil_gas_produced)
d
round(((d / t ) * 100), digits = 1)
```

San Joaquin Valley

```{r echo=FALSE, message=FALSE, warning=FALSE}
basin <- carb_basins %>%
  as_tibble() %>%
  filter(NAME == "San Joaquin Valley") %>%
  st_as_sf()
w <- wells_prod %>%
  st_intersection(basin)
p <- calgem_production %>% 
  filter(prod_month_year >= as.Date("2006-01-01")) %>%
  filter(latlong_id %in% w$latlong_id)
d <- sum(p$total_oil_gas_produced)
d
round(((d / t ) * 100), digits = 1)
```

South Central Coast

```{r echo=FALSE, message=FALSE, warning=FALSE}
basin <- carb_basins %>%
  as_tibble() %>%
  filter(NAME == "South Central Coast") %>%
  st_as_sf()
w <- wells_prod %>%
  st_intersection(basin)
p <- calgem_production %>% 
  filter(prod_month_year >= as.Date("2006-01-01")) %>%
  filter(latlong_id %in% w$latlong_id)
d <- sum(p$total_oil_gas_produced)
d
round(((d / t ) * 100), digits = 1)
```

South Coast

```{r echo=FALSE, message=FALSE, warning=FALSE}
basin <- carb_basins %>%
  as_tibble() %>%
  filter(NAME == "South Coast") %>%
  st_as_sf()
w <- wells_prod %>%
  st_intersection(basin)
p <- calgem_production %>% 
  filter(prod_month_year >= as.Date("2006-01-01")) %>%
  filter(latlong_id %in% w$latlong_id)
d <- sum(p$total_oil_gas_produced)
d
round(((d / t ) * 100), digits = 1)
```

**n wells by time**

2006-2009

```{r echo=FALSE}
d <- calgem_production %>%
  filter(total_oil_gas_produced > 0) %>%
  filter(prod_month_year >= as.Date("2006-01-01") &
           prod_month_year <= as.Date("2009-12-31")) %>%
  distinct(longitude, latitude, .keep_all = TRUE)
p <- calgem_production %>% 
  filter(total_oil_gas_produced > 0) %>%
  filter(prod_month_year >= as.Date("2006-01-01") &
           prod_month_year <= as.Date("2009-12-31")) %>%
  filter(latlong_id %in% w$latlong_id)
d <- sum(p$total_oil_gas_produced)
d
round(((d / t ) * 100), digits = 1)
```

2010-2014

```{r echo=FALSE}
d <- calgem_production %>%
  filter(total_oil_gas_produced > 0) %>%
  filter(prod_month_year >= as.Date("2010-01-01") &
           prod_month_year <= as.Date("2014-12-31")) %>%
  distinct(longitude, latitude, .keep_all = TRUE) 
p <- calgem_production %>% 
  filter(total_oil_gas_produced > 0) %>%
  filter(prod_month_year >= as.Date("2010-01-01") &
           prod_month_year <= as.Date("2014-12-31")) %>%
  filter(latlong_id %in% w$latlong_id)
d <- sum(p$total_oil_gas_produced)
d
round(((d / t ) * 100), digits = 1)
```

2015-2019

```{r echo=FALSE}
w <- calgem_production %>%
  filter(total_oil_gas_produced > 0) %>%
  filter(prod_month_year >= as.Date("2015-01-01") &
           prod_month_year <= as.Date("2019-12-31")) %>%
  distinct(longitude, latitude, .keep_all = T)
p <- calgem_production %>% 
  filter(total_oil_gas_produced > 0) %>%
  filter(prod_month_year >= as.Date("2015-01-01") &
           prod_month_year <= as.Date("2019-12-31")) %>%
  filter(latlong_id %in% w$latlong_id)
d <- sum(p$total_oil_gas_produced)
d
round(((d / t ) * 100), digits = 1)
```