---
title: "Crude oil production in California, 2020"
author: "David J.X. Gonzalez"
output: html_notebook
---

### Analysis for VISION, 4.1.2020


**Plot. WTI crude oil price, January 2019 - March 2020**

West Texas Intermediate crude oil prices. Prices from the Midway-Sunset field in California aren't available for March 2020 yet.

```{r echo=FALSE}
eia_wti_crude_price %>%
  filter(date >= as.Date("01-01-2019", format = "%m-%d-%Y")) %>% 
  filter(wti_crude_oil_price_per_barrel_usd > 0) %>%
  ggplot() +
    geom_line(aes(date, wti_crude_oil_price_per_barrel_usd)) +
    labs(x = "Date", y = "WTI Crude Oil Price per Barrel (USD)") +
    theme_classic()
```

**Plot. Oil production by month**

March data aren't available yet. Obtained from CalGEM website.

```{r echo=FALSE}
calgem_production_2020 %>%
  filter(prod_month_year < as.Date("05-01-2020", format = "%m-%d-%Y")) %>%
  group_by(prod_month_year) %>%
  summarize(oil_per_month = sum(oil_produced)) %>%
  ggplot() +
    geom_bar(aes(prod_month_year, oil_per_month), stat = "identity") +
    labs(x = "Date", y = "Oil Produced (Barrels)") +
    theme_classic()
```

**Plot. Wells spudded per month**

All wells data don't seem updated, no spud dates beyond December 2019 (except an eroneous date in 2026)

```{r echo=FALSE}
calgem_wells %>%
  filter(SpudDate >= as.Date("01-01-2020", format = "%m-%d-%Y"))# %>% View()
  group_by(month = month(SpudDate)) %>%
  summarize(spuds_per_month = n()) %>%
  ggplot() +
    geom_bar(aes(month, spuds_per_month), stat = "identity") +
    labs(x = "Date", y = "Oil Produced (Barrels)") +
    theme_classic()
```