---
title: "Ch. 3: Oil Production and Air Quality in California"
subtitle: "2020.02 - CalGEM Production Data"
output: html_notebook
---

```{r setup, include=FALSE}
# loads necessary packages and defines global variables
  source("../../code/0-setup/01-setup.R")

# loads additional packages
  library(ggrepel)  # for geom_label_repel()
```

```{r import, include=FALSE}
# imports raw data

  # California Air Resources Board (CARB) - administrative shapefiles
  carb_air_basins_raw <-
    st_read("../../data/raw/cal_epa/carb_air_basins/CaAirBasin.shp")
  
  # CalGEM - production, shapefiles
  calgem_fields_raw <- 
    st_read("../../data/raw/cal_gem/field_boundaries/DOGGR_Admin_Boundaries_Master.shp")
  calgem_production_2018_raw <-
    read_csv("../../data/raw/cal_gem/production/doggr_production_monthly_2018.csv")
  calgem_production_2019_raw <-
    read_csv("../../data/raw/cal_gem/production/doggr_production_monthly_2019.csv")
  
  # DrillingInfo - oil and gas well sites
  di_wells_raw <-
    read_csv("../../data/raw/drillinginfo/california_wells_jan2019.csv")
  
  # US Census Bureau - administrative shapefiles
  cal_counties_raw <- 
    st_read("../../data/raw/us_census/admin_shp/cal_counties.shp")
  us_states_raw <- 
    st_read("../../data/raw/us_census/admin_shp/tl_2018_us_state.shp")
  
# imports interim level
  
  # US EPA Air Quality System - air monitoring locations
  aqs_sites <- read_csv("../../data/interim/aqs_sites.csv")
```

```{r tidying, include=FALSE}
# loads functions for tidying the data
  source("../../code/2-tidying/02-tidy_drilling_data.R")
  source("../../code/2-tidying/03-tidy_production_data.R")

# converts AQS sites to sf object
aqs_sites <- aqs_sites %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# preps CalGEM fields data; needs to happen before prepDrillingData()
calgem_fields <- calgem_fields_raw %>%
  st_transform(crs_nad83) %>%
  # renames varible names
  mutate(field_object_id    = OBJECTID,  # not sure what this is
         field_name         = NAME,
         field_code         = FIELD_CODE,
         field_area_sq_mile = AREA_SQ_MI,
         field_area_acre    = AREA_ACRE,
         field_perimeter    = PERIMETER,
         field_start_date   = StartDate,
         field_end_date     = EndDate,
         district_name      = District) %>%
  # keeps only the variables we need
  select(field_object_id:district_name)
    
# calls functions to tidy all necessary datasets
  calgem_production_2018 <- prepProductionData(calgem_production_2018_raw)
  calgem_production_2019 <- prepProductionData(calgem_production_2019_raw)
  di_wells <- prepDrillingData(di_wells_raw) 

# prepares datasets necessary for this notebook
  
  # preps CARB air basins data
  carb_air_basins <- carb_air_basins_raw %>%
    st_transform(crs_nad83)
  
  # spatial join with oil fields data
  di_wells_fields <- di_wells %>%     
    st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
    st_join(calgem_fields) %>%
    as_tibble()
  
  # US Census
  cal_counties <- cal_counties_raw %>%
    st_transform(crs_nad83)
  us_states <- us_states_raw %>%
    st_transform(crs_nad83) 
```

```{r tidying2, echo=FALSE}
# makes combined dataset with oil wells and production by month, 2018-2019
wells_combined <- calgem_production_2018 %>%
  bind_rows(calgem_production_2019) %>%
  left_join(di_wells, by = "api_number")
```

**Questions to answer**
- Units of oil/water/gas produced?

# Description

- Range: January 2018 - December 2019 [Note: This range is due to how CalGEM reports the production data; a 'tidy' CSV of oil and gas production is reported for 2018-19; data prior to 2018 are available as Access Database files, which require cleaning.]

# Data Exploration

## Descriptive

- There are **`r wells_combined %>% distinct(api_number) %>% nrow()`**  unique wells in the combined DrillingInfo/CalGEM dataset (2018-2019).
- Distribution of oil produced across all wells and months
```{r echo=FALSE}
summary(wells_combined$oil_produced)
```

### Univariate 

#### Figure. Wells by county

```{r echo=FALSE}
wells_combined %>%
  group_by(county) %>%
  summarize(wells_per_county = n()) %>%
  
  # makes plot in descending order
  ggplot() +
    geom_bar(aes(x = reorder(county, wells_per_county), 
                 y = wells_per_county),
             stat = "identity") +
    labs(x = "County", y = "Count of Wells") +
    scale_y_continuous(position = "right") +  # arranges axis labels on top
    theme_bw() +
    coord_flip()
```

#### Figure. Map of oil and gas well locations in preproduction or production, 1999-2019

```{r echo=FALSE}
wells_buffer_1km <- di_wells %>%
  filter(drilled_1999_to_2019 == 1 | prod_1999_to_2019 == 1) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  st_transform(crs_projected) %>%
  st_buffer(1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
```

```{r echo=FALSE}
ggplot() +
  geom_sf(data = st_union(cal_counties), fill = "#FFFFFF") +
  geom_sf(data = wells_buffer_1km,fill = "orange", color = NA) +
  theme_bw()
```

#### Table. Monitors within 10 km of oil or gas wells

Note: This is different from the fields, defined below

```{r echo=FALSE}
wells_buffer_0.1km <- di_wells %>%
  filter(drilled_1999_to_2019 == 1 | prod_1999_to_2019 == 1) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  st_transform(crs_projected) %>%
  st_buffer(100) %>%
  st_union() %>%
  st_transform(crs_nad83)
```

#### Figure. Map of oil field locations (red)

```{r echo=FALSE}
ggplot() +
  geom_sf(data = st_union(cal_counties), fill = "#FFFFFF") +
  geom_sf(data = st_geometry(calgem_fields), fill = "red", color = NA) +
  theme_bw()
```

#### Figure. Map of locations of air quality monitors and (all) oil fields

```{r echo=FALSE}
# makes map
ggplot() +
  geom_sf(data = st_union(cal_counties), fill = "#FFFFFF") +
  geom_sf(data = calgem_fields, color = "red") +
  geom_sf(data = aqs_sites, shape = 1) +
  theme_bw()
```

#### Figure. Map of locations of air quality monitors and oil fields within at least within 10 km of one another

```{r echo=FALSE, message=FALSE, warning=FALSE}
# makes 10 km buffer around monitors
aqs_sites_buffer <- aqs_sites %>%
  st_transform(crs_projected) %>%
  st_buffer(10000) %>%
  st_transform(crs_nad83)

# restricts to oil fields near monitors
calgem_fields_near_monitors <- calgem_fields %>%
  st_intersection(aqs_sites_buffer)

# restricts to monitors near oil fields
aqs_sites_near_fields <- aqs_sites %>%
  st_intersection(calgem_fields_near_monitors)


# makes map
ggplot() +
  geom_sf(data = st_union(cal_counties), fill = "#FFFFFF") +
  geom_sf(data = calgem_fields_near_monitors, color = "red") +
  geom_sf(data = aqs_sites_near_fields, shape = 1) +
  theme_bw()
```

#### Table. Monitors with at least one oil field within 10 km

n = `r nrow(aqs_sites_near_fields)`

```{r echo=FALSE}
# prints list
aqs_sites_near_fields %>%
  mutate(Site.ID = site_id) %>%
  as_tibble() %>%
  select(Site.ID) %>%
  arrange(Site.ID)
```

#### Table. Oil fields with at least one monitor within 10 km

n = `r nrow(calgem_fields_near_monitors)`

```{r echo=FALSE}
# prints list
calgem_fields_near_monitors %>%
  mutate(Field.Name = field_name) %>%
  as_tibble() %>%
  select(Field.Name) %>%
  arrange(Field.Name)
```

#### Table. Count of well sites by field

Note: Well sites in preproduction and production are not mutually exclusive
```{r echo=FALSE, message=FALSE, warning=FALSE}
wells_combined %>%
  distinct(api_number, .keep_all = TRUE) %>%
  mutate(Field.Name = field_name) %>%
  group_by(Field.Name) %>%
  summarize(Well.Sites.in.Preproduction = sum(drilled_1999_to_2019),
            Well.Sites.in.Production = sum(prod_1999_to_2019),
            Well.Sites.All = n()) %>%
  arrange(-Well.Sites.All)
```


#### Table. Oil and gas production by field, sorted by oil production
 
```{r echo=FALSE, message=FALSE, warning=FALSE}
wells_combined %>%
  distinct(api_number, .keep_all = TRUE) %>%
  mutate(Field.Name = field_name) %>%
  group_by(Field.Name) %>%
  summarize(Total.Gas.Produced = sum(gas_produced),
            Total.Oil.Produced = sum(oil_produced)) %>%
  arrange(-Total.Oil.Produced)
```

#### Table. Oil and gas production by field, sorted by gas production
 
```{r echo=FALSE, message=FALSE, warning=FALSE}
wells_combined %>%
  distinct(api_number, .keep_all = TRUE) %>%
  mutate(Field.Name = field_name) %>%
  group_by(Field.Name) %>%
  summarize(Total.Gas.Produced = sum(gas_produced),
            Total.Oil.Produced = sum(oil_produced)) %>%
  arrange(-Total.Gas.Produced)
```

```{r include=FALSE}
ten_most_productive_fields <- c("Midway-Sunset", "Belridge, South", "Kern River", "Cymric", "Ojai", "Lost Hills", "San Ardo", "Wilmington", "Elk Hills", "Coalinga")
```

#### Figure. Distribution of wells by type

```{r echo=FALSE}
wells_combined %>%
  distinct(api_number, .keep_all = TRUE) %>%
  ggplot() +
    geom_bar(aes(as.factor(well_type))) +
    labs(x = "Well Type", y = "Count") +
    coord_flip() +
    theme_classic()
```

#### Figure. Wells spudded by month



#### Figure. Wells completed by month



#### Figure. Distribution of months producing

Data from Enverus

```{r echo=FALSE}
wells_combined %>%
  drop_na(prod_months) %>%
  ggplot() +
    geom_histogram(aes(prod_months), bins = 50) +
    labs(x = "Number of Months", y = "Count") +
    theme_classic()
```

#### Figure. Distribution of oil produced by well-month

The distribution of oil production by well-month is right-skewed and log-normal

```{r echo=FALSE}
wells_combined %>%
  ggplot() +
    geom_histogram(aes(log(oil_produced)), bins = 50) +
    labs(x = "Oil Produced (Units), Logarithmic Scale", y = "Count") +
    theme_classic()
```

#### Figure. Distribution of gas produced by well-month

The distribution of gas production by well-month is right-skewed and log-normal

```{r echo=FALSE}
wells_combined %>%
  ggplot() +
    geom_histogram(aes(log(gas_produced)), bins = 50) +
    labs(x = "Gas Produced (Units), Logarithmic Scale", y = "Count") +
    theme_classic()
```

#### Figure. Distribution of BTU of gas produced by well-month

The distribution of gas production by well-month is right-skewed and log-normal

```{r echo=FALSE}
wells_combined %>%
  ggplot() +
    geom_histogram(aes(gas_produced_btu), bins = 50) +
    labs(x = "BTU of Gas Produced (Units)", y = "Count") +
    theme_classic()
```

#### Figure. Distribution of API gravity of oil by well-month

From [Energy Insights](https://www.mckinseyenergyinsights.com/resources/refinery-reference-desk/api-gravity/) by McKinsey:

"API gravity is a commonly used index of the density of a crude oil or refined products. API stands for the American Petroleum Institute, which is the industry organization that created this measure. ¶ **Calculation of API gravity** ¶ API is calculated from a hydrocarbon's specific gravity using this formula: API = (141.5/Specific Gravity) - 131.5 ¶ **API gravity of crude oil grades** ¶ A crude oil will typically have an API between 15 and 45 degrees. Higher API indicates a lighter (lower density) crude. Lower API indicates a heavier (more dense) crude. Generally, lighter (high API) crudes are more valuable because they yield more high-value light products when run through a refinery. ¶ Light crude is typically in the 35-45 API range, which includes most of the highest valued crudes such as Brent and WTI. Crudes lighter than 45 are typically considered extra-light crude or condensates and are valued lower than light crude because they contain a lot of light ends such as propane and butane. A medium crude is in the 25-35 API range, and a heavy crude is in the 15-25 API range. Anything below 15 API would be considered an extra-heavy crude."

Interpretation: Most of the crude in this data set has a low API, indicating that it is mostly heavy (< 25) and extra-heavy crude (< 15). Many well-months have an API density of 0; I'm not sure whether that indicates an extra-heavy crude or missingness.

Note: The distribution of API density degrees extends beyond 100, with most < 400 and a few far above. I've set the range at 0-100 because this captures the majority of the relevant data.

```{r echo=FALSE}
wells_combined %>%
  ggplot() +
    geom_histogram(aes(APIGravityofOil), bins = 50) +
    labs(x = "API Gravity of Oil (Units)", y = "Count") +
    xlim(c(-10, 100)) +
    theme_classic()
```

#### Figure. Distribution of days producing by well-month

Generally, it appears that wells were either producing or not producing for the entire month. Note peaks at 28, 30, and 31 days, which correspond with month lengths.

```{r echo=FALSE}
wells_combined %>%
  ggplot() +
    geom_histogram(aes(DaysProducing), bins = 32) +
    labs(x = "Days Producing per Month", y = "Count") +
    theme_classic()
```

### Oil Production

#### Figure. Oil production by county

```{r echo=FALSE}
wells_combined %>%
  drop_na(oil_produced) %>%
  group_by(county) %>%
  summarize(oil_produced_by_county = sum(oil_produced)) %>%
  ggplot() +
    geom_bar(aes(x = reorder(county, oil_produced_by_county), 
                 y = oil_produced_by_county),
             stat = "identity") +
    labs(x = "County", y = "Oil Production") +
    scale_y_continuous(position = "right") +  # arranges axis labels on top
    theme_bw() +
    coord_flip()
```

#### Figure. Oil production by month, 2018-2019 (example wells)

Example of production at a select number of the wells in the dataset

```{r echo=FALSE}
wells_combined %>%
  # selects 
  filter(api_number %in% c("040192418400", "041112044800", "041112046100",
                           "041110105900", "040304517700", "041112062600",
                           "041112077100", "041112044400", "040590683200")) %>%
  ggplot() + 
    geom_bar(aes(prod_month_year, oil_produced), stat = "identity") + 
    facet_wrap(~ api_number) +
    labs(x = "Time", y = "Oil Produced (oil units?)") +
    theme_classic()
```

#### Figure. Oil production by month, 2018-2019 (all wells)

```{r echo=FALSE}
wells_combined %>%
  group_by(prod_month_year) %>%
  summarize(total_oil_produced_by_month = sum(oil_produced, na.rm = T)) %>%
  ggplot() + 
    geom_bar(aes(prod_month_year, total_oil_produced_by_month), 
             stat = "identity") +
    labs(x = "Time", y = "Oil Produced (oil units?)") +
    theme_classic()
```

#### Figure. Oil production by month and by county, 2018-2019 (all wells)

```{r echo=FALSE}
wells_combined %>%
  group_by(prod_month_year, county) %>%
  summarize(total_oil_produced_by_month = sum(oil_produced, na.rm = T)) %>%
  filter(county %in% c("Kern", "Ventura", "Los Angeles", "Monterey", "Fresno", 
                       "Santa Barbara", "Orange", "San Luis Obispo", "Kings", 
                       "Tulare")) %>%
  mutate(county = as.factor(county)) %>%
  ggplot() + 
    geom_bar(aes(prod_month_year, total_oil_produced_by_month), 
             stat = "identity") + 
    facet_wrap(~ county) +
    labs(x = "Time", y = "Oil Produced (oil units?)") +
    theme_classic()
```

#### Figure. Oil production by month and by field, 2018-2019 (ten most productive fields)

```{r echo=FALSE}
wells_combined %>%
  filter(field_name %in% ten_most_productive_fields) %>%  # list defined above
  group_by(prod_month_year, field_name) %>%
  summarize(total_oil_produced_by_month = sum(oil_produced, na.rm = T)) %>%
  mutate(field_name = as.factor(field_name)) %>%
  ggplot() + 
    geom_bar(aes(prod_month_year, total_oil_produced_by_month), 
             stat = "identity") + 
    facet_wrap(~ field_name) +
    labs(x = "Time", y = "Oil Produced (oil units?)") +
    theme_classic()
```

#### Figure. Oil production by month and by well type, 2018-2019

```{r echo=FALSE}
wells_combined %>%
  filter(well_type %in% c("CYCLIC STEAM", "OIL", "NA")) %>%
  drop_na(oil_produced) %>%
  ggplot() + 
    geom_bar(aes(prod_month_year, oil_produced), stat = "identity") + 
    facet_wrap(~ well_type) +
    labs(x = "Time", y = "Oil Produced (oil units?)") +
    theme_classic()
```

### Gas Production through Time

#### Figure. Gas production by county

```{r echo=FALSE}
wells_combined %>%
  drop_na(gas_produced) %>%
  group_by(county) %>%
  summarize(gas_produced_by_county = sum(gas_produced)) %>%
  ggplot() +
    geom_bar(aes(x = reorder(county, gas_produced_by_county), 
                 y = gas_produced_by_county),
             stat = "identity") +
    labs(x = "County", y = "Gas Production") +
    scale_y_continuous(position = "right") +  # arranges axis labels on top
    theme_bw() +
    coord_flip()
```

#### Figure. Gas production by month, 2018-2019 (all wells)

```{r echo=FALSE}
wells_combined %>%
  group_by(prod_month_year) %>%
  summarize(total_gas_produced_by_month = sum(gas_produced, na.rm = T)) %>%
  ggplot() + 
    geom_bar(aes(prod_month_year, total_gas_produced_by_month), 
             stat = "identity") +
    labs(x = "Time", y = "Gas Produced (gas units?)") +
    theme_classic()
```

#### Figure. Gas production by month and by county, 2018-2019 (all wells)

```{r echo=FALSE}
wells_combined %>%
  group_by(prod_month_year, county) %>%
  summarize(total_gas_produced_by_month = sum(gas_produced, na.rm = T)) %>%
  filter(county %in% c("Kern", "Butte", "San Joaquin", "Los Angeles", "Colusa",
                       "Solano", "Sacramento", "Glenn", "Yolo")) %>%
  mutate(county = as.factor(county)) %>%
  ggplot() + 
    geom_bar(aes(prod_month_year, total_gas_produced_by_month), 
             stat = "identity") + 
    facet_wrap(~ county) +
    labs(x = "Time", y = "Gas Produced (oil units?)") +
    theme_classic()
```

#### Figure. Gas production by month and by well type, 2018-2019

```{r echo=FALSE}
wells_combined %>%
  #filter(well_type %in% c("CYCLIC STEAM", "OIL", "NA")) %>%
  drop_na(gas_produced) %>%
  ggplot() + 
    geom_bar(aes(prod_month_year, gas_produced), stat = "identity") + 
    facet_wrap(~ well_type) +
    labs(x = "Time", y = "Gas Produced (gas units?)") +
    theme_classic()
```

### Bivariate

#### Figure. Relationship between oil and gas production by county

There appears to be a separation between oil and gas production by field. Fields that produce high volumes of oil tend to produce low volumes of gas, and vice-versa.

**Plot without labels**
 
```{r echo=FALSE, message=FALSE, warning=FALSE}
wells_combined %>%
  distinct(api_number, .keep_all = TRUE) %>%
  group_by(county) %>%
  summarize(Total.Gas.Produced = sum(gas_produced),
            Total.Oil.Produced = sum(oil_produced)) %>%
  ggplot() +
    geom_point(aes(Total.Oil.Produced, Total.Gas.Produced), alpha = 0.6) +
    theme_classic()
```
 
**Plot with labels**
 
```{r echo=FALSE, message=FALSE, warning=FALSE}
wells_combined %>%
  distinct(api_number, .keep_all = TRUE) %>%
  group_by(county) %>%
  summarize(Total.Gas.Produced = sum(gas_produced),
            Total.Oil.Produced = sum(oil_produced)) %>%
  ggplot(aes(Total.Oil.Produced, Total.Gas.Produced, label = county)) +
    #geom_label() +
    geom_label_repel(box.padding = 0.4, label.padding = 0.2, label.size = 0.3) +
    geom_point(alpha = 0.6) +
    theme_classic()
```

#### Figure. Relationship between oil and gas production by field

There appears to be a separation between oil and gas production by field. Fields that produce high volumes of oil tend to produce low volumes of gas, and vice-versa.
 
```{r echo=FALSE, message=FALSE, warning=FALSE}
wells_combined %>%
  distinct(api_number, .keep_all = TRUE) %>%
  mutate(Field.Name = field_name) %>%
  group_by(Field.Name) %>%
  summarize(Total.Gas.Produced = sum(gas_produced),
            Total.Oil.Produced = sum(oil_produced)) %>%
  ggplot() +
    geom_point(aes(Total.Oil.Produced, Total.Gas.Produced), alpha = 0.6) +
    theme_classic()
```


# Log

Note: Move to Ch. 3 project log

### 2.9.2020

**Questions to answer:**

  - What are the units of the oil/water/gas produced?
  - Does the production interval from Enverus/DrillingInfo match the data from CalGEM?

### 2.7.2020

- I was able to successfully make a 'wells_combined' dataset today, merging the Enverus/DrillingInfo data with the CalGEM production data for 2018 and 2019.
- To do this, I matched on API number. Note, the DrillingInfo dataset had API numbers with 13 characters/digits, and the CalGEM data had API numbers with 12 characters/digits. I had clipped the last digit of the API number from the DrillingInfo dataset, which appears to have been an extraneous 0.
- Total number of unique wells that we have production data for: **`r wells_combined %>% distinct(api_number) %>% nrow()`**

### 2.5.2020

As of today, I've obtained montly oil and gas production data for 2018 and 2019 from [this website](ftp://ftp.consrv.ca.gov/pub/oil/Online_Data/Production_Injection_Data/Pre-2018_Data_Format/) hosted by CalGEM These data are available as a CSV file. Older data (1997-2017) are available as Access databases.