---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}

```

```{r data_input, include=FALSE}
aqs_monitor_day <- readRDS("../../data/interim/aqs_monitor_day.rds")
aqs_monitor_day_exp_annuli_wind <- 
  readRDS("../../data/processed/aqs_monitor_day_exp_annuli_wind.rds")
carb_basin <- st_read("../../data/raw/cal_epa/carb_air_basins/CaAirBasin.shp") %>%
  st_transform(crs_nad83)
narr_precip <- readRDS("../../data/interim/narr_precipitation.rds")
narr_temp   <- readRDS("../../data/interim/narr_temperature.rds")
narr_wind   <- readRDS("../../data/interim/narr_wind.rds")
```

```{r data_tidying, include=FALSE}
# adds air basin to aqs_sites_
aqs_basins <- read_csv("../../data/interim/aqs_sites.csv") %>% 
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  st_join(carb_basin) %>%
  as_tibble() %>%
  select(site_id, NAME) %>%
  rename(carb_basin = NAME)

aqs_monitor_day <- aqs_monitor_day %>% 
  left_join(narr_precip, by = c("site_id", "date")) %>%
  left_join(narr_temp,   by = c("site_id", "date")) %>%
  left_join(narr_wind,   by = c("site_id", "date")) %>%
  left_join(aqs_basins,  by = "site_id")
```


```{r}
summary(wells_sf_new)
```


#### Plot. Distribution of mean daily wind direction, all sites

```{r echo=FALSE, message=FALSE, warning = FALSE}
aqs_monitor_day %>%
  drop_na(narr_wind_direction) %>%
  ggplot() +
  geom_histogram(aes(narr_wind_direction), bins = 360) +
  coord_polar(start = (-pi / 2), direction = -1) +
  scale_x_continuous(breaks = c(0, 90, 180, 270), limits = c(0, 360)) +
  labs(x = "", y = "") +
  theme_bw()
```


#### Plot. Distribution of mean daily wind direction by month

```{r echo=FALSE, message=FALSE, warning = FALSE}
aqs_monitor_day %>%
  drop_na(narr_wind_direction) %>%
  mutate(month = month(date)) %>%
  ggplot() +
  geom_histogram(aes(narr_wind_direction), bins = 360) +
  coord_polar(start = (-pi / 2), direction = -1) +
  scale_x_continuous(breaks = c(0, 90, 180, 270), limits = c(0, 360)) +
  facet_wrap(~ as.factor(month)) +
  labs(x = "", y = "") +
  theme_bw()
```

#### Plot. Distribution of mean daily wind direction by air basin

```{r echo=FALSE, warning = FALSE}
aqs_monitor_day %>%
  drop_na(narr_wind_direction) %>%
  ggplot() +
  geom_histogram(aes(narr_wind_direction), bins = 360) +
  coord_polar(start = (-pi / 2), direction = -1) +
  scale_x_continuous(breaks = c(0, 90, 180, 270), limits = c(0, 360)) +
  facet_wrap(~ as.factor(carb_basin)) +
  labs(x = "", y = "") +
  theme_bw()
```

### Bakersfield Oildale Monitor

Site ID: 060290232

#### Plot. Distribution of mean daily wind direction, Oildale (Bakersfield) site

```{r echo=FALSE, message=FALSE, warning = FALSE}
aqs_monitor_day %>%
  filter(site_id == "060290232") %>%
  drop_na(narr_wind_direction) %>%
  ggplot() +
  geom_histogram(aes(narr_wind_direction), bins = 360) +
  labs(x = "", y = "") +
  theme_bw()
```

#### Plot. Distribution of mean daily wind direction, Oildale (Bakersfield) site

```{r echo=FALSE, message=FALSE, warning = FALSE}
aqs_monitor_day %>%
  filter(site_id == "060290232") %>%
  summary()
drop_na(narr_wind_direction) %>%
  ggplot() +
  geom_histogram(aes(narr_wind_direction), bins = 360) +
  coord_polar(start = (-pi / 2), direction = -1) +
  scale_x_continuous(breaks = c(0, 90, 180, 270), limits = c(0, 360)) +
  labs(x = "", y = "") +
  theme_bw()
```

#### Plot. Wind rose

```{r echo=FALSE}
aqs_monitor_day %>%
  drop_na(wind_speed_daily_mean) %>%
  openair::windRose(wd  = "narr_wind_direction",
                     ws  = "narr_wind_speed")
```


```{r echo=FALSE}
aqs_monitor_day %>%
  drop_na(wind_speed_daily_mean) %>%
  openair::windRose(wd = "wind_direction_daily_mean",
                    ws = "wind_speed_daily_mean",
                    type = "season")
```


#### Plot. Distribution of mean daily wind direction by month

```{r echo=FALSE, message=FALSE, warning = FALSE}
aqs_monitor_day %>%
  filter(site_id == "060290232") %>%
  drop_na(narr_wind_direction) %>%
  mutate(month = month(date)) %>%
  ggplot() +
  geom_histogram(aes(narr_wind_direction), bins = 360) +
  coord_polar(start = (-pi / 2), direction = -1) +
  scale_x_continuous(breaks = c(0, 90, 180, 270), limits = c(0, 360)) +
  facet_wrap(~ as.factor(month)) +
  labs(x = "", y = "") +
  theme_bw()
```