# Roadmap to Raster Mapping

# Loading necessary packages
```{r}

library(ncdf4) 
library(sp)
library(raster)
library(rgdal) 
library(ggplot2)
library(readr)
library(dplyr)
library(sf)
library(knitr)
library(RNetCDF)
library(rasterVis)
library(tidyverse)

```

# setting knit working directory

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = 'C:\\Users\\Christina\\Documents\\Internships\\SURGE\\cal-drilling-air-quality')

```

# Opening and reading netCDF air temp data 

##following [this tutorial](https://community.rstudio.com/t/how-do-i-map-netcdf-files-in-r/35859) for rasterizing and mapping NetCDF files in R

### Opening data and assigning terms

```{r}

nc.air <- nc_open("data/raw/NARR/Daily_mean_surface_air_temperature/air.sfc.2019.nc")

print(nc.air)
attributes(nc.air$var)

lon.air <- ncvar_get(nc.air,"lon")
lat.air <- ncvar_get(nc.air,"lat")
time.air <- ncvar_get(nc.air, "time_bnds")
air <- ncvar_get(nc.air,"air")

#convert from Kelvin to degrees celsius

air <- air - 273.15

```

### Getting familiar

```{r}
dim(lon.air)
lon.air[c(1:8), c(1:5)]
attributes(nc.air$var$lon)

dim(lat.air)
lat.air[c(1:8), c(1:5)]
attributes(nc.air$var$lat)

dim(time.air)
time.air[c(1:2), c(1:8)]
attributes(nc.air$var$time_bnds)

dim(air)
air[c(1:8), c(1:5), 1]
attributes(nc.air$var$air)

```

### filling in missing values

```{r}
fill.air <- ncatt_get(nc.air, "air", "make_missing_value")
fill.air

nc_close(nc.air)


```

## Rasterizing and plotting netCDF air temp data

```{r}
# seubsetting air temp data for January 1st, 2019

air[air == fill.air$value] <- NA
air.slice <- air[,,1]
dim(air.slice)

```

```{r}
# rasterizeg subsetted netCDF air temp data
r <- raster(t(air.slice), xmn=min(lon.air), xmx=max(lon.air), ymn=min(lat.air), ymx=max(lat.air), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
r <- flip(r, direction='y')
```

## January 1st, 2019 mean air temp NARR data

```{r}
plot(r)
```

# Reading in aqs air monitor data - creating sf object

```{r}

#imports the data
aqs_sites <- read_csv("data/interim/aqs_sites.csv")

#selects only the columns we need
aqs_sites <- aqs_sites %>%
  dplyr::select(site_id, longitude, latitude)

# converts from tibble to sf object
aqs_sites_sf <- aqs_sites %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)


```

## plotting air monitor locations

```{r}
#visualize the aqs code
aqs_site_sf %>%
  ggplot() +
  geom_sf() +
  theme_bw()
```

# Extract air temp raster values from air monitor points

## Create raster stack of Jan-week1 data (JanStack) 

```{r}

Jan1slice <- air[,,1]
Jan1 <- raster::raster(t(Jan1slice), xmn=min(lon.air), xmx=max(lon.air), ymn=min(lat.air), ymx=max(lat.air), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
Jan1 <- flip(Jan1, direction='y')

Jan2slice <- air[,,2]
Jan2 <- raster(t(Jan2slice), xmn=min(lon.air), xmx=max(lon.air), ymn=min(lat.air), ymx=max(lat.air), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
Jan2 <- flip(Jan2, direction='y')

Jan3slice <- air[,,3]
Jan3 <- raster(t(Jan3slice), xmn=min(lon.air), xmx=max(lon.air), ymn=min(lat.air), ymx=max(lat.air), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
Jan3 <- flip(Jan3, direction='y')

Jan4slice <- air[,,4]
Jan4 <- raster(t(Jan4slice), xmn=min(lon.air), xmx=max(lon.air), ymn=min(lat.air), ymx=max(lat.air), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
Jan4 <- flip(Jan4, direction='y')

Jan5slice <- air[,,5]
Jan5 <- raster(t(Jan5slice), xmn=min(lon.air), xmx=max(lon.air), ymn=min(lat.air), ymx=max(lat.air), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
Jan5 <- flip(Jan5, direction='y')

Jan6slice <- air[,,6]
Jan6 <- raster(t(Jan2slice), xmn=min(lon.air), xmx=max(lon.air), ymn=min(lat.air), ymx=max(lat.air), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
Jan6 <- flip(Jan6, direction='y')

Jan7slice <- air[,,7]
Jan7 <- raster(t(Jan7slice), xmn=min(lon.air), xmx=max(lon.air), ymn=min(lat.air), ymx=max(lat.air), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
Jan7 <- flip(Jan7, direction='y')

JanStack <- stack(Jan1, Jan2, Jan3, Jan4, Jan5, Jan6, Jan7)


```


## Overlay and extract air temperature data, following [this tutorial]("https://gisday.wordpress.com/2014/03/24/extract-raster-values-from-points-using-r/comment-page-1/")

```{r}

rasvalue = raster::extract(JanStack, aqs_sites_sf)

#exporting result as a dataframe

PointData=cbind(aqs_sites_sf,rasvalue)

PointData1 <- rename(PointData, "site_id"=site_id, "Jan1"=layer.1, "Jan2"=layer.2, "Jan3"=layer.3, "Jan4"=layer.4, "Jan5"=layer.5, "Jan6"=layer.6, "Jan7"=layer.7)


```

## January week 1, 2019, mean air temperature data

```{r}
 
PointData1

```


# Opening and reading u/v wind vector data

## Opening u-wind data and assigning terms
```{r}
setwd("C:/Users/Christina/Documents/Internships/SURGE/cal-drilling-air-quality")

nc.windu <- nc_open("data/raw/narr/wind_u/uwnd.10m.2019.nc")

attributes(nc.windu$var)

lon.u <- ncvar_get(nc.windu,"lon")
lat.u <- ncvar_get(nc.windu,"lat")
time.u <- ncvar_get(nc.windu, "time_bnds")
uwnd <- ncvar_get(nc.windu,"uwnd")

```

## Getting to know u-wind data and filling in missing values

```{r}

dim(uwnd)
uwnd[c(1:2), c(1:2), c(1:5)]
attributes(nc.windu$var$uwnd)

fill.u <- ncatt_get(nc.windu, "uwnd", "make_missing_value")
fill.u

nc_close(nc.windu)

uwnd[uwnd == fill.u$value] <- NA

```

## Opening v-wind data and assigning terms

```{r}
setwd("C:/Users/Christina/Documents/Internships/SURGE/cal-drilling-air-quality")

nc.windv <- nc_open("data/raw/narr/wind_v/vwnd.10m.2019.nc")

attributes(nc.windv$var)

lon.v <- ncvar_get(nc.windv,"lon")
lat.v <- ncvar_get(nc.windv,"lat")
time.v <- ncvar_get(nc.windv, "time_bnds")
vwnd <- ncvar_get(nc.windv,"vwnd")

```

## Getting to know v-wind data and filling in missing values

```{r}
dim(vwnd)
vwnd[c(1:2), c(1:2), c(1:5)]
attributes(nc.windv$var$vwnd)

fill.v <- ncatt_get(nc.windv, "vwnd", "make_missing_value")
fill.v

nc_close(nc.windv)

vwnd[vwnd == fill.v$value] <- NA

```

# Rasterizing u-wind and v-wind component netCDF data

## Creating a raster stack of u-wind data for Jan-week1 (uStack)

```{r}

u1slice <- uwnd[,,1]
u1 <- raster::raster(t(u1slice), xmn=min(lon.u), xmx=max(lon.u), ymn=min(lat.u), ymx=max(lat.u), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
u1 <- flip(u1, direction='y')

u2slice <- uwnd[,,2]
u2 <- raster::raster(t(u2slice), xmn=min(lon.u), xmx=max(lon.u), ymn=min(lat.u), ymx=max(lat.u), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
u2 <- flip(u2, direction='y')

u3slice <- uwnd[,,3]
u3 <- raster::raster(t(u3slice), xmn=min(lon.u), xmx=max(lon.u), ymn=min(lat.u), ymx=max(lat.u), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
u3 <- flip(u3, direction='y')

u4slice <- uwnd[,,4]
u4 <- raster::raster(t(u4slice), xmn=min(lon.u), xmx=max(lon.u), ymn=min(lat.u), ymx=max(lat.u), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
u4 <- flip(u4, direction='y')

u5slice <- uwnd[,,5]
u5 <- raster::raster(t(u1slice), xmn=min(lon.u), xmx=max(lon.u), ymn=min(lat.u), ymx=max(lat.u), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
u5 <- flip(u5, direction='y')

u6slice <- uwnd[,,6]
u6 <- raster::raster(t(u6slice), xmn=min(lon.u), xmx=max(lon.u), ymn=min(lat.u), ymx=max(lat.u), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
u6 <- flip(u6, direction='y')

u7slice <- uwnd[,,7]
u7 <- raster::raster(t(u7slice), xmn=min(lon.u), xmx=max(lon.u), ymn=min(lat.u), ymx=max(lat.u), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
u7 <- flip(u7, direction='y')

uStack <- stack(u1, u2, u3, u4, u5, u6, u7)
```


## Creating a raster stack of v-wind data for Jan-week1

```{r}

v1slice <- vwnd[,,1]
v1 <- raster::raster(t(v1slice), xmn=min(lon.v), xmx=max(lon.v), ymn=min(lat.v), ymx=max(lat.v), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
v1 <- flip(v1, direction='y')

v2slice <- vwnd[,,2]
v2 <- raster::raster(t(v2slice), xmn=min(lon.v), xmx=max(lon.v), ymn=min(lat.v), ymx=max(lat.v), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
v2 <- flip(v2, direction='y')

v3slice <- vwnd[,,3]
v3 <- raster::raster(t(v3slice), xmn=min(lon.v), xmx=max(lon.v), ymn=min(lat.v), ymx=max(lat.v), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
v3 <- flip(v3, direction='y')

v4slice <- vwnd[,,4]
v4 <- raster::raster(t(v4slice), xmn=min(lon.v), xmx=max(lon.v), ymn=min(lat.v), ymx=max(lat.v), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
v4 <- flip(v4, direction='y')

v5slice <- vwnd[,,5]
v5 <- raster::raster(t(v1slice), xmn=min(lon.v), xmx=max(lon.v), ymn=min(lat.v), ymx=max(lat.v), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
v5 <- flip(v5, direction='y')

v6slice <- vwnd[,,6]
v6 <- raster::raster(t(v6slice), xmn=min(lon.v), xmx=max(lon.v), ymn=min(lat.v), ymx=max(lat.v), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
v6 <- flip(v6, direction='y')

v7slice <- vwnd[,,7]
v7 <- raster::raster(t(v7slice), xmn=min(lon.v), xmx=max(lon.v), ymn=min(lat.v), ymx=max(lat.v), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))
v7 <- flip(v7, direction='y')

vStack <- stack(v1, v2, v3, v4, v5, v6, v7)

```

# calculating wind direction and speed for week 1 Jan 2019

## calculating wind speed and wind direction
```{r}
ws.1.week1.2019 <- sqrt(uStack^2+vStack^2)
wd.1.week1.2019 <- (((180/pi)*(atan2(uStack,vStack)))+180)


```

## reviewing wind direction data

```{r}
class(wd.1.week1.2019)

dim(wd.1.week1.2019)

wd.1.week1.2019

```
# extract wind raster values and from aqs points

## extract wind speed from aqs points, and export to data table

```{r}
rasws = raster::extract(ws.1.week1.2019, aqs_site_sf)

Janweek1ws=cbind(aqs_site_sf,rasws)

Janweek1ws <- rename(Janweek1ws, "site_id"=site_id, "1/1/19"=layer.1, "1/2/19"=layer.2, "1/3/19"=layer.3, "1/4/19"=layer.4, "1/5/19"=layer.5, "1/6/19"=layer.6, "1/7/19"=layer.7)

```


## extract wind direction from aqs points, and export to data table
```{r}

raswd = raster::extract(wd.1.week1.2019, aqs_site_sf)

Janweek1wd=cbind(aqs_site_sf,raswd)

Janweek1wd <- rename(Janweek1wd, "site_id"=site_id, "1/1/19"=layer.1, "1/2/19"=layer.2, "1/3/19"=layer.3, "1/4/19"=layer.4, "1/5/19"=layer.5, "1/6/19"=layer.6, "1/7/19"=layer.7)

```

## Wind direction from aqs points, January week 1, 2019

```{r}
Janweek1wd
```

##  Wind speed from aqs points, January week 1, 2019
```{r}
Janweek1ws
```

## merging SF data frames, converting from wide to long structure

```{r}

Janweek1wd <- Janweek1wd %>%
 pivot_longer(
   cols = starts_with("1/"),
   names_to = "Jan.date",
   values_to = "wind_direction",
   values_drop_na = TRUE)

Janweek1ws <- Janweek1ws %>%
 pivot_longer(
   cols = starts_with("1/"),
   names_to = "Jan.date",
   values_to = "wind_speed",
   values_drop_na = TRUE)



```

```{r}
Janweek1wind <-cbind(Janweek1wd, Janweek1ws)

Janweek1wind <- Janweek1wind[, !duplicated(colnames(Janweek1wind))]

```


# Creating a single upwind wedge based on wind direction and magnitude

## merging narr_wind and search datasets

```{r}
search_w <- lef

```


## subsetting monitor coordinates for a single air monitor day

```{r}
#creating subset of a single air monitor

monitor_1 <- dplyr::filter(Janweek1wind, Jan.date == '1/1/19' & site_id == '060010003')

monitor_coord <- monitor_1 %>%
    mutate(lat = unlist(map(monitor_1$geometry,1)),
           long = unlist(map(monitor_1$geometry,2)))

monitor_coord <- monitor_coord %>% dplyr::select(-geometry) %>%  as.tibble(monitor_coord)

monitor_coord
  
```

## calculating upwind vector point from wind direction and magnitude

### calculating upwind vector and creating a matrix
```{r}
upwind <- matrix(c('060010003','upwind','1/1/19',NA,NA,
                (monitor_coord$lat + 
                   ((15/110.574) * cos(monitor_coord$wind_direction))),
                (monitor_coord$long + 
                   ((15/110.574)*sin(monitor_coord$wind_direction)))),
                ncol=7, byrow=TRUE)

colnames(upwind) <- c('site_id', 'point',
                      'Jan.date', 'wind_direction',
                      'wind_speed', 'lat', 'long') 

upwind <- as.tibble(upwind)

upwind$wind_direction <- as.numeric(upwind$wind_direction)
upwind$wind_speed <- as.numeric(upwind$wind_speed)
upwind$lat <- as.numeric(upwind$lat)
upwind$long <- as.numeric(upwind$long)

upwind

```

## creating new east and west upwind extensions, using calculated magnitude (15km/cos(45))

```{r}
#west
upwindextent_west <- matrix(c('60010003','west_extent','1/1/19',NA,NA,
                (monitor_coord$lat + 
                   (((15/110.574)/cos(45))* 
                       cos(monitor_coord$wind_direction + 45))),
                 (monitor_coord$long + 
                   (((15/110.574)/cos(45))*
                       sin(monitor_coord$wind_direction + 45)))),
                ncol=7, byrow=TRUE)

colnames(upwindextent_west) <- c('site_id', 'point', 
                                 'Jan.date', 'wind_direction', 
                                 'wind_speed', 'lat', 'long')

upwindextent_west <- as.tibble(upwindextent_west)

upwindextent_west$wind_direction <- as.numeric(upwindextent_west$wind_direction)

upwindextent_west$wind_speed <- as.numeric(upwindextent_west$wind_speed)

upwindextent_west$lat <- as.numeric(upwindextent_west$lat)

upwindextent_west$long <- as.numeric(upwindextent_west$long) 

upwindextent_west

#east

upwindextent_east <- matrix(c('60010003','east_extent','1/1/19',NA,NA,
                (monitor_coord$lat + 
                   (((15/110.574)/cos(45)) *
                       cos(monitor_coord$wind_direction - 45))),
                 (monitor_coord$long + 
                   (((15/110.574)/cos(45))*
                       sin(monitor_coord$wind_direction - 45)))),
                ncol=7, byrow=TRUE)

colnames(upwindextent_east) <- c('site_id', 'point', 
                                 'Jan.date', 'wind_direction', 
                                 'wind_speed', 'lat', 'long')

upwindextent_east <- as.tibble(upwindextent_east)

upwindextent_east$wind_direction <- as.numeric(upwindextent_east$wind_direction)

upwindextent_east$wind_speed <- as.numeric(upwindextent_east$wind_speed)

upwindextent_east$lat <- as.numeric(upwindextent_east$lat)

upwindextent_east$long <- as.numeric(upwindextent_east$long)

upwindextent_east

```

## plotting the upwind tangent line with a 45 degree extent, using calculated magnitude

```{r}
upwindtangent <- full_join(upwindextent_east, upwindextent_west) %>% full_join(y = upwind) 

upwindtangent <- 
  full_join(upwindextent_east, upwindextent_west) %>% 
  full_join(y = upwind)


upwindtangent_sf <- upwindtangent %>% 
  st_as_sf(coords = c("lat", "long"), crs = 4326)

upwindtangent_sf %>% ggplot() +
   geom_sf() +
   theme_bw()

```


## selecting only coordinate data
```{r}
upwindextent_east_coord <- upwindextent_east %>% dplyr::select(lat, long)
upwindextent_west_coord <- upwindextent_west %>% dplyr::select(lat, long)
monitor_coord2 <- monitor_coord %>% dplyr::select(lat, long)
upwind_coord <- upwind %>% dplyr::select(lat, long)

```

```{r}
monitor_coord_sf <- monitor_coord2 %>% 
  st_as_sf(coords = c("lat", "long"), crs = 4326)

```


## merging coordinates to create east and west tibbles
```{r}
windvector_east_coord <- full_join(upwindextent_east_coord, upwind_coord) %>% full_join(y = monitor_coord2) 

windvector_west_coord <- full_join(upwindextent_west_coord, upwind_coord) %>% full_join(y = monitor_coord2) 

```


## creating the wedge

```{r}
windvector_east_coord_sf <- st_as_sf(windvector_east_coord, coords = c("lat", "long"))

st_crs(windvector_east_coord_sf) <- 4326

windvector_east_polygon <- windvector_east_coord_sf %>% st_coordinates() %>% st_multipoint() %>% 
  st_cast("POLYGON") 

east_wedge <- st_sfc(east_wedge, crs = 4326)

ggplot() +
     geom_sf(data=windvector_east_polygon) +
     theme_bw()

windvector_west_coord_sf <- st_as_sf(windvector_west_coord, coords = c("lat", "long"))

st_crs(windvector_west_coord_sf) <- 4326

windvector_west_polygon <- windvector_west_coord_sf %>% st_coordinates() %>% st_multipoint() %>% 
  st_cast("POLYGON") 

west_wedge <- st_sfc(windvector_west_polygon, crs = 4326)

ggplot() +
     geom_sf(data=west_wedge) +
     theme_bw()

wedge <- st_union(east_wedge, west_wedge)

ggplot() +
     geom_sf(data=wedge) +
     theme_bw()

```

## plotting annuli, monitor locations, and the wedge

```{r}

ggplot() +
     geom_sf(data=wedge) +
     geom_sf(data=monitor_coord_sf) +
     theme_bw()

```


# STOP - excess


## Looping through the raster fxn

```{r}

# write a function to process one day's slice of NARR data
narrExtraction <- function(daily_slice) {
  
  daily_obs <- raster::raster(t(daily_slice), 
                              xmn = min(lon), xmx = max(lon), 
                              ymn = min(lat), ymx = max(lat), 
                              crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 
                                 +no_defs +towgs84=0,0,0")) %>%
    flip(direction = 'y')
  
  return(daily_obs)
}

# define a list to capture the data
my_data <- list()

# write a loop to call the function
for (i in c(1:365)) {
    my_data[i] <- narrExtraction(air[, , i])  
}

my_data
```




```{r}
my_data <- as.data.frame(cbind(x = c(1:10), y = c(11:20)))
my_data
```


<<<<<<< HEAD

```{r}
for(i in c(1:10)) {
  var <- sum(my_data[i, 1], 100)
  print(var)
}
```
=======
>>>>>>> 3bef10223ef8b54149a04f6c0ca9479839e0127c

