---
title: "Results - Daily Annuli - Preproduction - PM2.5"
output: html_notebook
---

*add prelimn exposure assessments for prod volume*

```{r setup, include=FALSE}
source("../../code/0-setup/1-setup.R")
library("lfe")
```

```{r input_data, include=FALSE}
aqs_daily_annuli_exposure <- 
  readRDS("../../data/processed/aqs_daily_annuli_exposure.rds")
```

```{r setup_data, include=FALSE}
data_in <- aqs_daily_annuli_exposure %>%
  filter(pm10_mean >= 0) %>%
  filter(year %in% c(2006:2019))
```

## Primary results

#### Adjusted linear regression model without FE

```{r echo=FALSE}
model_fit <- felm(pm10_mean ~ 
                    preprod_count_uw_0to1km +
                    preprod_count_uw_1to2km +
                    preprod_count_uw_2to3km +
                    preprod_count_uw_3to4km +
                    preprod_count_uw_4to5km +
                    preprod_count_uw_5to6km +
                    preprod_count_uw_6to7km +
                    preprod_count_uw_7to8km +
                    preprod_count_uw_8to9km +
                    preprod_count_uw_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    n_plume +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed |
                    factor(day_of_week),
                  data = data_in)
summary(model_fit)
```


#### Adjusted linear regression model with month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(pm10_mean ~ 
                    preprod_count_uw_0to1km +
                    preprod_count_uw_1to2km +
                    preprod_count_uw_2to3km +
                    preprod_count_uw_3to4km +
                    preprod_count_uw_4to5km +
                    preprod_count_uw_5to6km +
                    preprod_count_uw_6to7km +
                    preprod_count_uw_7to8km +
                    preprod_count_uw_8to9km +
                    preprod_count_uw_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    n_plume +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | factor(day_of_week) +
                    factor(month) +
                    factor(carb_basin):factor(year),
                  data = data_in)
summary(model_fit)
```


#### Adjusted linear regression model with monitor + month + basin:year FE

**Primary result**

```{r echo=FALSE}
model_fit <- felm(pm10_mean ~ 
                    preprod_count_uw_0to1km +
                    preprod_count_uw_1to2km +
                    preprod_count_uw_2to3km +
                    preprod_count_uw_3to4km +
                    preprod_count_uw_4to5km +
                    preprod_count_uw_5to6km +
                    preprod_count_uw_6to7km +
                    preprod_count_uw_7to8km +
                    preprod_count_uw_8to9km +
                    preprod_count_uw_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    n_plume +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | factor(day_of_week) +
                    factor(carb_basin):factor(month) +
                    factor(carb_basin):factor(year) +
                    monitor_id,
                  data = data_in)
summary(model_fit)
```


**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind"),
    point_est = coef(model_fit)[1:20],
    ci_lower  = confint(model_fit)[1:20],
    ci_upper  = confint(model_fit)[25:44])
write_csv(model_output, "point_estimates/daily_annuli_preproduction_pm10.csv")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper,
                      color = direction)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily CO conc. (µg/m^3)") +
  theme_classic()
```


#### Adjusted linear regression model with monitor + month + basin:year FE and polynomial terms

```{r echo=FALSE}
model_fit <- felm(pm10_mean ~ 
                    preprod_count_uw_0to1km +
                    poly(preprod_count_uw_1to2km, 2) +
                    poly(preprod_count_uw_2to3km, 2) +
                    poly(preprod_count_uw_3to4km, 2) +
                    poly(preprod_count_uw_4to5km, 2) +
                    poly(preprod_count_uw_5to6km, 2) +
                    poly(preprod_count_uw_6to7km, 2) +
                    poly(preprod_count_uw_7to8km, 2) +
                    poly(preprod_count_uw_8to9km, 2) +
                    poly(preprod_count_uw_9to10km, 2) +
                    preprod_count_dw_0to1km +
                    poly(preprod_count_dw_1to2km, 2) +
                    poly(preprod_count_dw_2to3km, 2) +
                    poly(preprod_count_dw_3to4km, 2) +
                    poly(preprod_count_dw_4to5km, 2) +
                    poly(preprod_count_dw_5to6km, 2) +
                    poly(preprod_count_dw_6to7km, 2) +
                    poly(preprod_count_dw_7to8km, 2) +
                    poly(preprod_count_dw_8to9km , 2) +
                    poly(preprod_count_dw_9to10km, 2) +
                    n_plume +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month) +
                    factor(carb_basin):factor(year),
                  data = data_in)
summary(model_fit)
```



## No wind

#### Adjusted linear regression model with monitor + month + basin:year FE

**For sensitivity analysis**

```{r echo=FALSE}
model_fit <- felm(pm10_mean ~ 
                    preprod_count_nowind_0to1km +
                    preprod_count_nowind_1to2km +
                    preprod_count_nowind_2to3km +
                    preprod_count_nowind_3to4km +
                    preprod_count_nowind_4to5km +
                    preprod_count_nowind_5to6km +
                    preprod_count_nowind_6to7km +
                    preprod_count_nowind_7to8km +
                    preprod_count_nowind_8to9km +
                    preprod_count_nowind_9to10km +
                    n_plume +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | factor(day_of_week) +
                    factor(carb_basin):factor(month) +
                    factor(carb_basin):factor(year) +
                    monitor_id ,
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5"),
    point_est = coef(model_fit)[1:5],
    ci_lower  = confint(model_fit)[1:5],
    ci_upper  = confint(model_fit)[15:19])
write_csv(model_output, "point_estimates/daily_annuli_preproduction_pm10_nowind.csv")
model_output
```

## Robustness checks

### Excluding smoke days

#### Adjusted linear regression model with monitor + month + basin:year FE

**Excluding days with smoke plumes overhead**

```{r echo=FALSE}
model_fit <- felm(pm10_mean ~ 
                    preprod_count_uw_0to1km +
                    preprod_count_uw_1to2km +
                    preprod_count_uw_2to3km +
                    preprod_count_uw_3to4km +
                    preprod_count_uw_4to5km +
                    preprod_count_uw_5to6km +
                    preprod_count_uw_6to7km +
                    preprod_count_uw_7to8km +
                    preprod_count_uw_8to9km +
                    preprod_count_uw_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | factor(day_of_week) +
                    factor(carb_basin):factor(month) +
                    factor(carb_basin):factor(year) +
                    monitor_id,
                  data = subset(data_in, smoke_day == 0))
summary(model_fit)
```

```{r echo=FALSE}
results_preprod_25_nosmokedays <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind"),
    point_est = coef(model_fit)[1:20],
    ci_lower  = confint(model_fit)[1:20],
    ci_upper  = confint(model_fit)[24:43])
write_csv(results_preprod_25_nosmokedays,
          "point_estimates/daily_annuli_preproduction_pm10_nosmokedays.csv")
results_preprod_25_nosmokedays
```

#### Plot

```{r echo=FALSE}
panel_1 <- results_preprod_25_nosmokedays %>%
  filter(distance == c("0-1", "1-2", "2-3", "3-4", "4-5")) %>%
  filter(direction == "Upwind") %>%
  mutate(distance_ordinal = c(1:5)) %>%
  ggplot() + 
  geom_ribbon(aes(x     = distance_ordinal,
                  y     = point_est,
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "#08519c",
              alpha = 0.5) +
  geom_pointrange(aes(x     = distance_ordinal,
                      y     = point_est,
                      ymin  = ci_lower, 
                      ymax  = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  ylim(c(-1, 4.7)) +
  labs(x = "Distance to well", y = expression(PM[2.5]*" "*(µg*" "*m^-3))) +
  scale_x_discrete(name = "Distance to well",
                   limits = c("0-1", "1-2", "2-3", "3-4", "4-5")) +
  theme_classic() +
  theme(legend.position = "none",
        axis.line.y  = element_blank())

panel_2 <- results_preprod_25_nosmokedays %>%
  filter(distance == c("0-1", "1-2", "2-3", "3-4", "4-5")) %>%
  filter(direction == "Downwind") %>%
  mutate(distance_ordinal = c(1:5)) %>%
  ggplot() + 
  geom_ribbon(aes(x     = distance_ordinal,
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "#9ecae1", 
              alpha = 0.5) +
  geom_pointrange(aes(x     = distance_ordinal, 
                      y     = point_est, 
                      ymin  = ci_lower, 
                      ymax  = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well", y = "") +
  scale_x_discrete(name = "Distance to well", 
                   limits = c("0-1", "1-2", "2-3", "3-4", "4-5")) +
  scale_y_continuous(position = "right", limits = c(-1, 4.7)) +
  theme_classic() +
  theme(axis.line.y = element_blank(),
        axis.text.y = element_blank())

figure <- panel_1 + panel_2
figure
ggsave(filename = "figure_s3_pm10_nosmokedays.png", plot = figure, device = "png",
       height = 3, width = 8,
       path = "../../output/figures/")
```



## Stratified analyses

### Geographic - urban/rural

#### Urban - Adjusted linear regression model with monitor + month + basin:year FE

```{r}
data_in2 <- data_in %>%
  filter(is_urban == 1)
model_fit <- felm(pm10_mean ~ 
                    preprod_count_uw_0to1km +
                    preprod_count_uw_1to2km +
                    preprod_count_uw_2to3km +
                    preprod_count_uw_3to4km +
                    preprod_count_uw_4to5km +
                    preprod_count_uw_5to6km +
                    preprod_count_uw_6to7km +
                    preprod_count_uw_7to8km +
                    preprod_count_uw_8to9km +
                    preprod_count_uw_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    n_plume +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | factor(day_of_week) +
                    factor(month) +
                    factor(carb_basin):factor(year) +
                    monitor_id ,
                  data = data_in2)
summary(model_fit)
```

#### Rural - Adjusted linear regression model with monitor + month + basin:year FE

```{r}
data_in2 <- data_in %>%
  filter(is_urban == 0)
model_fit <- felm(pm10_mean ~ 
                    preprod_count_uw_0to1km +
                    preprod_count_uw_1to2km +
                    preprod_count_uw_2to3km +
                    preprod_count_uw_3to4km +
                    preprod_count_uw_4to5km +
                    preprod_count_uw_5to6km +
                    preprod_count_uw_6to7km +
                    preprod_count_uw_7to8km +
                    preprod_count_uw_8to9km +
                    preprod_count_uw_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    n_plume +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | factor(day_of_week) +
                    factor(month) +
                    factor(carb_basin):factor(year) +
                    monitor_id ,
                  data = data_in2)
summary(model_fit)
```

### Geographic - CARB basins

```{r}

```

### Temporal - 5-year increments

```{r}

```


