---
title: "Results - Daily Annuli - Preproduction - CO"
output: html_notebook
---

*add prelimn exposure assessments for prod volume*

```{r setup, include=FALSE}
source("../../code/0-setup/1-setup.R")
library("lfe")
```

```{r input_data, include=FALSE}
aqs_daily_annuli_exposure <- 
  readRDS("../../data/processed/aqs_daily_annuli_exposure.rds")
```

```{r setup_data, include=FALSE}
data_in <- aqs_daily_annuli_exposure %>%
  filter(co_max >= 0) %>%
  filter(year %in% c(2006:2019))
```

## Primary results

#### Unadjusted linear regression model without FE

```{r echo=FALSE}
model_fit <- glm(co_max ~ 
                    preprod_count_uw_0to1km +
                    preprod_count_uw_1to2km +
                    preprod_count_uw_2to3km +
                    preprod_count_uw_3to4km +
                    preprod_count_uw_4to5km +
                    preprod_count_uw_5to6km +
                    preprod_count_uw_6to7km +
                    preprod_count_uw_7to8km +
                    preprod_count_uw_8to9km +
                    preprod_count_uw_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    preprod_count_lateral_0to1km +
                    preprod_count_lateral_1to2km +
                    preprod_count_lateral_2to3km +
                    preprod_count_lateral_3to4km +
                    preprod_count_lateral_4to5km +
                    preprod_count_lateral_5to6km +
                    preprod_count_lateral_6to7km +
                    preprod_count_lateral_7to8km +
                    preprod_count_lateral_8to9km +
                    preprod_count_lateral_9to10km,
                  data = data_in)
summary(model_fit)
```

#### Adjusted linear regression model without FE

```{r echo=FALSE}
model_fit <- felm(co_max ~ 
                    preprod_count_uw_0to1km +
                    preprod_count_uw_1to2km +
                    preprod_count_uw_2to3km +
                    preprod_count_uw_3to4km +
                    preprod_count_uw_4to5km +
                    preprod_count_uw_5to6km +
                    preprod_count_uw_6to7km +
                    preprod_count_uw_7to8km +
                    preprod_count_uw_8to9km +
                    preprod_count_uw_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +               
                    preprod_count_lateral_0to1km +
                    preprod_count_lateral_1to2km +
                    preprod_count_lateral_2to3km +
                    preprod_count_lateral_3to4km +
                    preprod_count_lateral_4to5km +
                    preprod_count_lateral_5to6km +
                    preprod_count_lateral_6to7km +
                    preprod_count_lateral_7to8km +
                    preprod_count_lateral_8to9km +
                    preprod_count_lateral_9to10km +
                    n_plume +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | day_of_week,
                  data = data_in)
summary(model_fit)
```


#### Adjusted linear regression model with month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(co_max ~ 
                    preprod_count_uw_0to1km +
                    preprod_count_uw_1to2km +
                    preprod_count_uw_2to3km +
                    preprod_count_uw_3to4km +
                    preprod_count_uw_4to5km +
                    preprod_count_uw_5to6km +
                    preprod_count_uw_6to7km +
                    preprod_count_uw_7to8km +
                    preprod_count_uw_8to9km +
                    preprod_count_uw_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +               
                    preprod_count_lateral_0to1km +
                    preprod_count_lateral_1to2km +
                    preprod_count_lateral_2to3km +
                    preprod_count_lateral_3to4km +
                    preprod_count_lateral_4to5km +
                    preprod_count_lateral_5to6km +
                    preprod_count_lateral_6to7km +
                    preprod_count_lateral_7to8km +
                    preprod_count_lateral_8to9km +
                    preprod_count_lateral_9to10km +
                    n_plume +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | day_of_week +
                    factor(monitor_id):factor(month) +
                    factor(carb_basin):factor(year),
                  data = data_in)
summary(model_fit)
```


#### Adjusted linear regression model with monitor + month + basin:year FE

**Primary result**

```{r echo=FALSE}
model_fit <- felm(co_max ~ 
                    preprod_count_uw_0to1km +
                    preprod_count_uw_1to2km +
                    preprod_count_uw_2to3km +
                    preprod_count_uw_3to4km +
                    preprod_count_uw_4to5km +
                    preprod_count_uw_5to6km +
                    preprod_count_uw_6to7km +
                    preprod_count_uw_7to8km +
                    preprod_count_uw_8to9km +
                    preprod_count_uw_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    preprod_count_lateral_0to1km +
                    preprod_count_lateral_1to2km +
                    preprod_count_lateral_2to3km +
                    preprod_count_lateral_3to4km +
                    preprod_count_lateral_4to5km +
                    preprod_count_lateral_5to6km +
                    preprod_count_lateral_6to7km +
                    preprod_count_lateral_7to8km +
                    preprod_count_lateral_8to9km +
                    preprod_count_lateral_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed +
                    n_plume
                  | day_of_week + 
                    factor(monitor_id):factor(month) +
                    factor(carb_basin):factor(year) +
                    monitor_id,
                  data = data_in)
summary(model_fit)
```


**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Lateral", "Lateral", "Lateral", "Lateral","Lateral",
                  "Lateral", "Lateral", "Lateral", "Lateral","Lateral"),
    point_est = coef(model_fit)[1:30],
    ci_lower  = confint(model_fit)[1:30],
    ci_upper  = confint(model_fit)[35:64])
write_csv(model_output, "point_estimates/daily_annuli_preproduction_co.csv")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily CO conc. (µg/m^3)") +
  theme_classic() +
  facet_wrap(~ direction)
```

## No wind

#### Adjusted linear regression model with monitor + month + basin:year FE

**For sensitivity analysis**

```{r echo=FALSE}
model_fit <- felm(co_max ~ 
                    preprod_count_nowind_0to1km +
                    preprod_count_nowind_1to2km +
                    preprod_count_nowind_2to3km +
                    preprod_count_nowind_3to4km +
                    preprod_count_nowind_4to5km +
                    preprod_count_nowind_5to6km +
                    preprod_count_nowind_6to7km +
                    preprod_count_nowind_7to8km +
                    preprod_count_nowind_8to9km +
                    preprod_count_nowind_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed +
                    n_plume
                  | factor(day_of_week) +
                    factor(monitor_id):factor(month) +
                    factor(monitor_id):factor(year) +
                    monitor_id ,
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5"),
    point_est = coef(model_fit)[1:5],
    ci_lower  = confint(model_fit)[1:5],
    ci_upper  = confint(model_fit)[15:19])
write_csv(model_output, "point_estimates/daily_annuli_preproduction_co_nowind.csv")
model_output
```

#### Adjusted linear regression model with monitor + month + basin:year FE and polynomial terms

```{r echo=FALSE}
model_fit <- felm(co_max ~ 
                    preprod_count_uw_0to1km +
                    poly(preprod_count_uw_1to2km, 2) +
                    poly(preprod_count_uw_2to3km, 2) +
                    poly(preprod_count_uw_3to4km, 2) +
                    poly(preprod_count_uw_4to5km, 2) +
                    poly(preprod_count_uw_5to6km, 2) +
                    poly(preprod_count_uw_6to7km, 2) +
                    poly(preprod_count_uw_7to8km, 2) +
                    poly(preprod_count_uw_8to9km, 2) +
                    poly(preprod_count_uw_9to10km, 2) +
                    preprod_count_dw_0to1km +
                    poly(preprod_count_dw_1to2km, 2) +
                    poly(preprod_count_dw_2to3km, 2) +
                    poly(preprod_count_dw_3to4km, 2) +
                    poly(preprod_count_dw_4to5km, 2) +
                    poly(preprod_count_dw_5to6km, 2) +
                    poly(preprod_count_dw_6to7km, 2) +
                    poly(preprod_count_dw_7to8km, 2) +
                    poly(preprod_count_dw_8to9km , 2) +
                    poly(preprod_count_dw_9to10km, 2) +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | day_of_week + 
                    factor(month) +
                    factor(carb_basin):factor(year) +
                    monitor_id,
                  data = data_in)
summary(model_fit)
```