---
title: "Results - Daily Annuli Upwind New Wells"
subtitle: "Stratified by Air Basin"
output: html_notebook
---

```{r setup, include=FALSE}
source("../../code/0-setup/1-setup.R")
library("lfe")
```

```{r input_data_components, include=FALSE}
aqs_daily_annuli_preprod_downwind <-
  readRDS("../../data/processed/aqs_daily_annuli_preproduction_downwind.rds") %>%
  rename(preprod_count_dw_0to1km  = wells_new_0to1km,
         preprod_count_dw_1to2km  = wells_new_1to2km,
         preprod_count_dw_2to3km  = wells_new_2to3km,
         preprod_count_dw_3to4km  = wells_new_3to4km,
         preprod_count_dw_4to5km  = wells_new_4to5km,
         preprod_count_dw_5to6km  = wells_new_5to6km,
         preprod_count_dw_6to7km  = wells_new_6to7km,
         preprod_count_dw_7to8km  = wells_new_7to8km,
         preprod_count_dw_8to9km  = wells_new_8to9km,
         preprod_count_dw_9to10km = wells_new_9to10km) %>%
  select(-(wells_new_10to11km:wells_new_14to15km))
aqs_daily_annuli_preprod_upwind <- 
  readRDS("../../data/processed/aqs_daily_annuli_upwind_preprod.rds") %>%
  select(-(wells_new_10to11km:wells_new_14to15km))
carb_basins <- st_read("../../data/raw/cal_epa/carb_air_basins/CaAirBasin.shp") %>%
  st_transform(crs_nad83)
aqs_sites_sacramento <- read_rds("../../data/interim/aqs_sites.rds") %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  st_intersection(st_geometry(subset(carb_basins, NAME == "San Joaquin Valley"))) %>%
  as_tibble() %>%
  select(monitor_id)
aqs_sites_san_joaquin <- read_rds("../../data/interim/aqs_sites.rds") %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  st_intersection(st_geometry(subset(carb_basins, NAME == "San Joaquin Valley"))) %>%
  as_tibble() %>%
  select(monitor_id)
aqs_sites_south_central_coast <- read_rds("../../data/interim/aqs_sites.rds") %>% 
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  st_intersection(st_geometry(subset(carb_basins, NAME == "South Central Coast"))) %>%
  as_tibble() %>%
  select(monitor_id)
aqs_sites_south_coast <- read_rds("../../data/interim/aqs_sites.rds") %>% 
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  st_intersection(st_geometry(subset(carb_basins, NAME == "South Coast"))) %>%
  as_tibble() %>%
  select(monitor_id)
wells_sf <- readRDS("../../data/interim/wells_interim.rds") %>%
  filter(preprod_1999_to_2019 == 1) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)
```


# Gases

## Pollutant: Nitrogen Dioxide (NO2)

### San Joaquin Valley

**Descriptive statistics:**

- n monitor days = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>% filter(no2_concentration_daily_max >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>% filter(no2_concentration_daily_max >= 0) %>% distinct(monitor_id) %>% nrow()`

```{r include=FALSE}
covars <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>%
  filter(no2_concentration_daily_max >= 0) %>%
  inner_join(aqs_daily_annuli_preprod_downwind) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-no2_concentration_daily_max)
data_in <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>%
  filter(no2_concentration_daily_max >= 0) %>%
  group_by(monitor_day) %>%
  summarize(no2_concentration_daily_max = 
              mean(no2_concentration_daily_max)) %>%
  left_join(covars, by = "monitor_day")
```


#### Adjusted linear regression model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(no2_concentration_daily_max ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    narr_precip +
                    narr_temp +
                    narr_wind_direction
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    distance_ordinal = c(1:10, 1:10), 
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind"),
    point_est = coef(model_fit)[1:20],
    ci_lower  = confint(model_fit)[1:20],
    ci_upper  = confint(model_fit)[24:43])
saveRDS(model_output, file = "upwind_downwind_preprod_gases_no2_san_joaquin.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
panel_no2_san_joaquin <- ggplot() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_ribbon(data = subset(model_output, direction == "Downwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "gold3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Downwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "gold3", alpha = 0.5) + 
  geom_ribbon(data = subset(model_output, direction == "Upwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "purple3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Upwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "purple3", alpha = 0.5) + 
  labs(y = "") +
  scale_x_discrete(name = "Distance to well (km)", 
                   limits = c("0-1", "1-2", "2-3", "3-4", "4-5",
                              "5-6", "6-7", "7-8", "8-9", "9-10")) +
  theme_classic() +
  theme(legend.position = "none")
panel_no2_san_joaquin
```


### South Coast

**Descriptive statistics:**

- n monitor days = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>% filter(no2_concentration_daily_max >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>% filter(no2_concentration_daily_max >= 0) %>% distinct(monitor_id) %>% nrow()`

```{r include=FALSE}
# removes duplicat
covars <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>%
  filter(no2_concentration_daily_max >= 0) %>%
  inner_join(aqs_daily_annuli_preprod_downwind) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-no2_concentration_daily_max)
data_in <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>%
  filter(no2_concentration_daily_max >= 0) %>%
  group_by(monitor_day) %>%
  summarize(no2_concentration_daily_max = 
              mean(no2_concentration_daily_max)) %>%
  left_join(covars, by = "monitor_day")
```


#### Adjusted linear regression model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(no2_concentration_daily_max ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    narr_precip +
                    narr_temp +
                    narr_wind_direction
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    distance_ordinal = c(1:10, 1:10), 
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind"),
    point_est = coef(model_fit)[1:20],
    ci_lower  = confint(model_fit)[1:20],
    ci_upper  = confint(model_fit)[24:43])
saveRDS(model_output, file = "upwind_downwind_preprod_gases_no2_south_coast.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
panel_no2_south_coast <- ggplot() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_ribbon(data = subset(model_output, direction == "Downwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "gold3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Downwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "gold3", alpha = 0.5) + 
  geom_ribbon(data = subset(model_output, direction == "Upwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "purple3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Upwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "purple3", alpha = 0.5) + 
  labs(y = "") +
  scale_x_discrete(name = "Distance to well (km)", 
                   limits = c("0-1", "1-2", "2-3", "3-4", "4-5",
                              "5-6", "6-7", "7-8", "8-9", "9-10")) +
  theme_classic() +
  theme(legend.position = "none")
panel_no2_south_coast
```


## Pollutant: Ozone (O3)

### San Joaquin

**Descriptive statistics:**

- n monitor days = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>% filter(o3_concentration_daily_max >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>% filter(o3_concentration_daily_max >= 0) %>% distinct(monitor_id) %>% nrow()`


```{r include=FALSE}
covars <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>%
  filter(o3_concentration_daily_max >= 0) %>%
  inner_join(aqs_daily_annuli_preprod_downwind) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-o3_concentration_daily_max)
data_in <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>%
  filter(o3_concentration_daily_max >= 0) %>%
  group_by(monitor_day) %>%
  summarize(o3_concentration_daily_max = 
              mean(o3_concentration_daily_max)) %>%
  left_join(covars, by = "monitor_day")
```

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(o3_concentration_daily_max ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    narr_precip +
                    narr_temp +
                    narr_wind_direction
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```


**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    distance_ordinal = c(1:10, 1:10), 
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind"),
    point_est = coef(model_fit)[1:20],
    ci_lower  = confint(model_fit)[1:20],
    ci_upper  = confint(model_fit)[24:43])
saveRDS(model_output, file = "upwind_downwind_preprod_gases_o3_san_joaquin.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
panel_o3_san_joaquin <- ggplot() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_ribbon(data = subset(model_output, direction == "Downwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "gold3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Downwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "gold3", alpha = 0.5) + 
  geom_ribbon(data = subset(model_output, direction == "Upwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "purple3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Upwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "purple3", alpha = 0.5) + 
  labs(y = "") +
  scale_x_discrete(name = "Distance to well (km)", 
                   limits = c("0-1", "1-2", "2-3", "3-4", "4-5",
                              "5-6", "6-7", "7-8", "8-9", "9-10")) +
  theme_classic() +
  theme(legend.position = "none")
panel_o3_san_joaquin
```


### South Coast

**Descriptive statistics:**

- n monitor days = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>% filter(o3_concentration_daily_max >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>% filter(o3_concentration_daily_max >= 0) %>% distinct(monitor_id) %>% nrow()`


```{r include=FALSE}
covars <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>%
  filter(o3_concentration_daily_max >= 0) %>%
  inner_join(aqs_daily_annuli_preprod_downwind) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-o3_concentration_daily_max)
data_in <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>%
  filter(o3_concentration_daily_max >= 0) %>%
  group_by(monitor_day) %>%
  summarize(o3_concentration_daily_max = 
              mean(o3_concentration_daily_max)) %>%
  left_join(covars, by = "monitor_day")
```

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(o3_concentration_daily_max ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    narr_precip +
                    narr_temp +
                    narr_wind_direction
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```


**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    distance_ordinal = c(1:10, 1:10), 
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind"),
    point_est = coef(model_fit)[1:20],
    ci_lower  = confint(model_fit)[1:20],
    ci_upper  = confint(model_fit)[24:43])
saveRDS(model_output, file = "upwind_downwind_preprod_gases_o3_south_coast.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
panel_o3_south_coast <- ggplot() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_ribbon(data = subset(model_output, direction == "Downwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "gold3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Downwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "gold3", alpha = 0.5) + 
  geom_ribbon(data = subset(model_output, direction == "Upwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "purple3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Upwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "purple3", alpha = 0.5) + 
  labs(y = "") +
  scale_x_discrete(name = "Distance to well (km)", 
                   limits = c("0-1", "1-2", "2-3", "3-4", "4-5",
                              "5-6", "6-7", "7-8", "8-9", "9-10")) +
  theme_classic() +
  theme(legend.position = "none")
panel_o3_south_coast
```


**Count of new wells within 1-km bins of O3 monitors**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preprod_upwind %>% 
  filter(o3_concentration_daily_max >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "Distance from monitor (km)", y = "n wells") +
  theme_classic()
```


## Pollutant: Sulfur Dioxide (SO2)

::::explore missing data::::

### San Joaquin

**Descriptive statistics:**

- n monitor days = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>% filter(so2_concentration_daily_max >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>% filter(so2_concentration_daily_max >= 0) %>% distinct(monitor_id) %>% nrow()`

```{r include=FALSE}
covars <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>%
  filter(so2_concentration_daily_max >= 0) %>%
  inner_join(aqs_daily_annuli_preprod_downwind) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-so2_concentration_daily_max)
data_in <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>%
  filter(so2_concentration_daily_max >= 0) %>%
  group_by(monitor_day) %>%
  summarize(so2_concentration_daily_max = 
              mean(so2_concentration_daily_max)) %>%
  left_join(covars, by = "monitor_day")
```

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(so2_concentration_daily_max ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    distance_ordinal = c(1:10, 1:10), 
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind"),
    point_est = coef(model_fit)[1:20],
    ci_lower  = confint(model_fit)[1:20],
    ci_upper  = confint(model_fit)[24:43])
saveRDS(model_output, file = "upwind_downwind_preprod_gases_so2_san_joaquin.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
panel_so2_san_joaquin <- ggplot() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_ribbon(data = subset(model_output, direction == "Downwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "gold3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Downwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "gold3", alpha = 0.5) + 
  geom_ribbon(data = subset(model_output, direction == "Upwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "purple3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Upwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "purple3", alpha = 0.5) + 
  labs(y = "") +
  scale_x_discrete(name = "Distance to well (km)", 
                   limits = c("0-1", "1-2", "2-3", "3-4", "4-5",
                              "5-6", "6-7", "7-8", "8-9", "9-10")) +
  theme_classic() +
  theme(legend.position = "none")
panel_so2_san_joaquin
```

*Note: There are insufficient data on SO2 in San Joaquin Valley to do this analysis*

### South Coast

**Descriptive statistics:**

- n monitor days = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>% filter(so2_concentration_daily_max >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>% filter(so2_concentration_daily_max >= 0) %>% distinct(monitor_id) %>% nrow()`

```{r include=FALSE}
covars <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>%
  filter(so2_concentration_daily_max >= 0) %>%
  inner_join(aqs_daily_annuli_preprod_downwind) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-so2_concentration_daily_max)
data_in <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>%
  filter(so2_concentration_daily_max >= 0) %>%
  group_by(monitor_day) %>%
  summarize(so2_concentration_daily_max = 
              mean(so2_concentration_daily_max)) %>%
  left_join(covars, by = "monitor_day")
```

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(so2_concentration_daily_max ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    distance_ordinal = c(1:10, 1:10), 
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind"),
    point_est = coef(model_fit)[1:20],
    ci_lower  = confint(model_fit)[1:20],
    ci_upper  = confint(model_fit)[24:43])
saveRDS(model_output, file = "upwind_downwind_preprod_gases_so2_south_coast.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
panel_so2_south_coast<- ggplot() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_ribbon(data = subset(model_output, direction == "Downwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "gold3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Downwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "gold3", alpha = 0.5) + 
  geom_ribbon(data = subset(model_output, direction == "Upwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "purple3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Upwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "purple3", alpha = 0.5) + 
  labs(y = "") +
  scale_x_discrete(name = "Distance to well (km)", 
                   limits = c("0-1", "1-2", "2-3", "3-4", "4-5",
                              "5-6", "6-7", "7-8", "8-9", "9-10")) +
  theme_classic() +
  theme(legend.position = "none")
panel_so2_south_coast
```


**Count of new wells within 1-km bins of SO2 monitors**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preprod_upwind %>% 
  filter(so2_concentration_daily_max >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
figure_3b <- well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "", y = "") +
  scale_y_continuous(position = "right") +
  theme_classic() +
  theme(axis.line    = element_blank(),  # removes x-axis
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
figure_3b

ggsave(filename = "figure_3b_gases_so2.png", 
       plot = figure_3b, device = "png",
       height = 1, width = 7,
       path = "../../output/figures/")
```


# Particulate Matter

## Pollutant: Fine particulate matter (PM2.5)

### San Joaquin

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>% filter(pm2.5_concentration_daily_mean >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>% filter(pm2.5_concentration_daily_mean >= 0) %>% distinct(monitor_id) %>% nrow()`

```{r include=FALSE}
# removes duplicat
covars <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>%
  filter(pm2.5_concentration_daily_mean >= 0) %>% 
  inner_join(aqs_daily_annuli_preprod_downwind) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-pm2.5_concentration_daily_mean)
data_in <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_san_joaquin$monitor_id) %>%
  filter(pm2.5_concentration_daily_mean >= 0) %>%
  group_by(monitor_day) %>%
  summarize(pm2.5_concentration_daily_mean = 
              mean(pm2.5_concentration_daily_mean)) %>%
  left_join(covars, by = "monitor_day")
```


#### Adjusted linear regression model with monitor + month + basin:year FE adjusted for temp + precip

```{r echo=FALSE}
model_fit <- felm(pm2.5_concentration_daily_mean ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    distance_ordinal = c(1:10, 1:10), 
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind"),
    point_est = coef(model_fit)[1:20],
    ci_lower  = confint(model_fit)[1:20],
    ci_upper  = confint(model_fit)[24:43])
saveRDS(model_output, file = "upwind_downwind_preprod_gases_pm25_san_joaquin.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
panel_pm25_san_joaquin <- ggplot() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_ribbon(data = subset(model_output, direction == "Downwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "gold3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Downwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "gold3", alpha = 0.5) + 
  geom_ribbon(data = subset(model_output, direction == "Upwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "purple3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Upwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "purple3", alpha = 0.5) + 
  labs(y = "") +
  scale_x_discrete(name = "Distance to well (km)", 
                   limits = c("0-1", "1-2", "2-3", "3-4", "4-5",
                              "5-6", "6-7", "7-8", "8-9", "9-10")) +
  theme_classic() +
  theme(legend.position = "none")
panel_pm25_san_joaquin
```


### South Coast

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>% filter(pm2.5_concentration_daily_mean >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>% filter(pm2.5_concentration_daily_mean >= 0) %>% distinct(monitor_id) %>% nrow()`

```{r include=FALSE}
# removes duplicat
covars <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>%
  filter(pm2.5_concentration_daily_mean >= 0) %>% 
  inner_join(aqs_daily_annuli_preprod_downwind) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-pm2.5_concentration_daily_mean)
data_in <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>%
  filter(pm2.5_concentration_daily_mean >= 0) %>%
  group_by(monitor_day) %>%
  summarize(pm2.5_concentration_daily_mean = 
              mean(pm2.5_concentration_daily_mean)) %>%
  left_join(covars, by = "monitor_day")
```


#### Adjusted linear regression model with monitor + month + basin:year FE adjusted for temp + precip

```{r echo=FALSE}
model_fit <- felm(pm2.5_concentration_daily_mean ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```


**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    distance_ordinal = c(1:10, 1:10), 
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind"),
    point_est = coef(model_fit)[1:20],
    ci_lower  = confint(model_fit)[1:20],
    ci_upper  = confint(model_fit)[24:43])
saveRDS(model_output, file = "upwind_downwind_preprod_gases_pm25_south_coast.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
panel_pm25_south_coast <- ggplot() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_ribbon(data = subset(model_output, direction == "Downwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "gold3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Downwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "gold3", alpha = 0.5) + 
  geom_ribbon(data = subset(model_output, direction == "Upwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "purple3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Upwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "purple3", alpha = 0.5) + 
  labs(y = "") +
  scale_x_discrete(name = "Distance to well (km)", 
                   limits = c("0-1", "1-2", "2-3", "3-4", "4-5",
                              "5-6", "6-7", "7-8", "8-9", "9-10")) +
  theme_classic() +
  theme(legend.position = "none")
panel_pm25_south_coast
```



**Count of new wells within 1-km bins of PM2.5 monitors**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preprod_upwind %>% 
  filter(pm2.5_concentration_daily_mean >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "Distance from monitor (km)", y = "n wells") +
  theme_classic()
```



# VOCs

## Pollutant: Total NMOC

### South Coast

**Descriptive statistics:**

- n monitor days = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>% filter(total_nmoc >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preprod_upwind %>% filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>% filter(total_nmoc >= 0) %>% distinct(monitor_id) %>% nrow()`


```{r include=FALSE}
covars <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>%
  filter(total_nmoc >= 0) %>%
  inner_join(aqs_daily_annuli_preprod_downwind) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-total_nmoc)
data_in <- aqs_daily_annuli_preprod_upwind %>%
  filter(monitor_id %in% aqs_sites_south_coast$monitor_id) %>%
  filter(total_nmoc >= 0) %>%
  group_by(monitor_day) %>%
  summarize(total_nmoc = 
              mean(total_nmoc)) %>%
  left_join(covars, by = "monitor_day")
```


#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(total_nmoc ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    preprod_count_dw_0to1km +
                    preprod_count_dw_1to2km +
                    preprod_count_dw_2to3km +
                    preprod_count_dw_3to4km +
                    preprod_count_dw_4to5km +
                    preprod_count_dw_5to6km +
                    preprod_count_dw_6to7km +
                    preprod_count_dw_7to8km +
                    preprod_count_dw_8to9km +
                    preprod_count_dw_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    distance_ordinal = c(1:10, 1:10), 
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind"),
    point_est = coef(model_fit)[1:20],
    ci_lower  = confint(model_fit)[1:20],
    ci_upper  = confint(model_fit)[24:43])
saveRDS(model_output, file = "upwind_downwind_preprod_vocs_nmoc_south_coast.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
panel_vocs_nmoc_south_coast <- ggplot() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_ribbon(data = subset(model_output, direction == "Downwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "gold3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Downwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "gold3", alpha = 0.5) + 
  geom_ribbon(data = subset(model_output, direction == "Upwind"),
              aes(x     = distance_ordinal, 
                  y     = point_est, 
                  ymin  = ci_lower, 
                  ymax  = ci_upper),
              fill = "purple3", 
              alpha = 0.2) +
  geom_line(data = subset(model_output, direction == "Upwind"),
             aes(x = distance_ordinal, y = point_est),
             color = "purple3", alpha = 0.5) + 
  labs(y = "") +
  scale_x_discrete(name = "Distance to well (km)", 
                   limits = c("0-1", "1-2", "2-3", "3-4", "4-5",
                              "5-6", "6-7", "7-8", "8-9", "9-10")) +
  theme_classic() +
  theme(legend.position = "none")
panel_vocs_nmoc_south_coast
```


**Count of new wells within 1-km bins of monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preprod_upwind %>% 
  filter(total_nmoc >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
figure_3b <- well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "", y = "") +
  scale_y_continuous(position = "right") +
  theme_classic() +
  theme(axis.line    = element_blank(),  # removes x-axis
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
figure_3b

ggsave(filename = "figure_3b_vocs_nmoc.png", 
       plot = figure_3b, device = "png",
       height = 1, width = 7,
       path = "../../output/figures/")
```


