---
title: "Results - Daily Annuli Upwind New Wells"
output: html_notebook
---

```{r setup, include=FALSE}
source("../../code/0-setup/1-setup.R")
library("lfe")
```

```{r input_data, include=FALSE}
wells_sf    <- readRDS("../../data/interim/wells_interim.rds") %>%
  filter(preprod_1999_to_2019 == 1) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)
```


# Gases

## Pollutant: Carbon monoxide (CO)

```{r include=FALSE}
# removes duplicat
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(co_concentration_daily_max >= 0) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-co_concentration_daily_max)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(co_concentration_daily_max >= 0) %>%
  group_by(monitor_day) %>%
  summarize(co_concentration_daily_max = 
              mean(co_concentration_daily_max)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(co_concentration_daily_max >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(co_concentration_daily_max >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(co_concentration_daily_max ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    narr_precip + 
                    narr_temp
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = subset(aqs_daily_annuli_preproduction_uw, 
                                co_concentration_daily_max > 0))
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[13:22])
saveRDS(model_output, file = "upwind_new_co.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily CO conc. (µg/m^3)") +
  theme_classic()
```

**Count of new wells within 1-km bins of CO monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(co_concentration_daily_max >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "Distance from monitor (km)", y = "n wells") +
  theme_classic()
```


## Pollutant: NO

```{r include=FALSE}
# removes duplicat
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(no_concentration_daily_max >= 0) %>%
  inner_join(aqs_daily_annuli_preproduction_dw) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-no_concentration_daily_max)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(no_concentration_daily_max >= 0) %>%
  group_by(monitor_day) %>%
  summarize(no_concentration_daily_max = 
              mean(no_concentration_daily_max)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(no_concentration_daily_max >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(no_concentration_daily_max >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(no_concentration_daily_max ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    narr_precip +
                    narr_temp
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Upwind**

*Table*

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[23:32])
saveRDS(model_output, file = "upwind_preprod_gases_no.rds")
model_output
```

*Figure*

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily NO") +
  theme_classic()
```

**Count of new wells within 1-km bins of CO monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(no_concentration_daily_max >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
figure_3b <- well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "", y = "") +
  scale_y_continuous(position = "right") +
  theme_classic() +
  theme(axis.line    = element_blank(),  # removes x-axis
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
figure_3b

ggsave(filename = "figure_3b_gases_no.png", 
       plot = figure_3b, device = "png",
       height = 1, width = 7,
       path = "../../output/figures/")
```

## Pollutant: NO2

```{r include=FALSE}
# removes duplicat
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(no2_concentration_daily_max >= 0) %>%
  inner_join(aqs_daily_annuli_preproduction_dw) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-no2_concentration_daily_max)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(no2_concentration_daily_max >= 0) %>%
  group_by(monitor_day) %>%
  summarize(no2_concentration_daily_max = 
              mean(no2_concentration_daily_max)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(no2_concentration_daily_max >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(no2_concentration_daily_max >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Adjusted linear regression model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(no2_concentration_daily_max ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    wells_dw_new_0to1km +
                    wells_dw_new_1to2km +
                    wells_dw_new_2to3km +
                    wells_dw_new_3to4km +
                    wells_dw_new_4to5km +
                    wells_dw_new_5to6km +
                    wells_dw_new_6to7km +
                    wells_dw_new_7to8km +
                    wells_dw_new_8to9km +
                    wells_dw_new_9to10km +
                    narr_precip +
                    narr_temp
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Upwind**

*Table*

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[23:32])
saveRDS(model_output, file = "upwind_preprod_gases_no2.rds")
model_output
```

*Figure*

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily NO2") +
  theme_classic()
```

**Downwind**

*Table*

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Downwind",
    point_est = coef(model_fit)[11:20],
    ci_lower  = confint(model_fit)[11:20],
    ci_upper  = confint(model_fit)[33:42])
saveRDS(model_output, file = "downwind_preprod_gases_no2.rds")
model_output
```

*Figure*

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily NO2") +
  theme_classic()
```


## Pollutant: Ozone (O3)

```{r include=FALSE}
# removes duplicat
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(o3_concentration_daily_max >= 0) %>%
  inner_join(aqs_daily_annuli_preproduction_dw) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-o3_concentration_daily_max)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(o3_concentration_daily_max >= 0) %>%
  group_by(monitor_day) %>%
  summarize(o3_concentration_daily_max = 
              mean(o3_concentration_daily_max)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(o3_concentration_daily_max >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(o3_concentration_daily_max >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(o3_concentration_daily_max ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    wells_dw_new_0to1km +
                    wells_dw_new_1to2km +
                    wells_dw_new_2to3km +
                    wells_dw_new_3to4km +
                    wells_dw_new_4to5km +
                    wells_dw_new_5to6km +
                    wells_dw_new_6to7km +
                    wells_dw_new_7to8km +
                    wells_dw_new_8to9km +
                    wells_dw_new_9to10km +
                    narr_precip +
                    narr_temp
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Upwind**

*Table*

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[23:32])
saveRDS(model_output, file = "upwind_preprod_gases_o3.rds")
model_output
```

*Figure*

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily ozone conc.") +
  theme_classic()
```

**Downwind**

*Table*

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Downwind",
    point_est = coef(model_fit)[11:20],
    ci_lower  = confint(model_fit)[11:20],
    ci_upper  = confint(model_fit)[33:42])
saveRDS(model_output, file = "downwind_preprod_gases_o3.rds")
model_output
```

*Figure*

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily ozone conc.") +
  theme_classic()
```


**Count of new wells within 1-km bins of O3 monitors**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(o3_concentration_daily_max >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "Distance from monitor (km)", y = "n wells") +
  theme_classic()
```


## Pollutant: Sulfur Dioxide (SO2)

::::explore missing data::::

```{r include=FALSE}
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(so2_concentration_daily_max >= 0) %>%
  inner_join(aqs_daily_annuli_preproduction_dw) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-so2_concentration_daily_max)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(so2_concentration_daily_max >= 0) %>%
  group_by(monitor_day) %>%
  summarize(so2_concentration_daily_max = 
              mean(so2_concentration_daily_max)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(so2_concentration_daily_max >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(so2_concentration_daily_max >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(so2_concentration_daily_max ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    wells_dw_new_0to1km +
                    wells_dw_new_1to2km +
                    wells_dw_new_2to3km +
                    wells_dw_new_3to4km +
                    wells_dw_new_4to5km +
                    wells_dw_new_5to6km +
                    wells_dw_new_6to7km +
                    wells_dw_new_7to8km +
                    wells_dw_new_8to9km +
                    wells_dw_new_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Upwind**

*Table*

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[24:33]
  )
saveRDS(model_output, file = "upwind_preprod_gases_so2.rds")
model_output
```

*Figure*

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily SO2 conc. (units)") +
  theme_classic()
```

**Downwind**

*Table*

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Downwind",
    point_est = coef(model_fit)[11:20],
    ci_lower  = confint(model_fit)[11:20],
    ci_upper  = confint(model_fit)[34:43]
  )
saveRDS(model_output, file = "downwind_preprod_gases_so2.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily SO2 conc. (units)") +
  theme_classic()
```

**Count of new wells within 1-km bins of CO monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(so2_concentration_daily_max >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
figure_3b <- well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "", y = "") +
  scale_y_continuous(position = "right") +
  theme_classic() +
  theme(axis.line    = element_blank(),  # removes x-axis
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
figure_3b

ggsave(filename = "figure_3b_gases_so2.png", 
       plot = figure_3b, device = "png",
       height = 1, width = 7,
       path = "../../output/figures/")
```


# Particulate Matter

## Pollutant: Fine particulate matter (PM2.5)

```{r include=FALSE}
# removes duplicat
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(pm2.5_concentration_daily_mean >= 0) %>% 
  inner_join(aqs_daily_annuli_preproduction_dw) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-pm2.5_concentration_daily_mean)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(pm2.5_concentration_daily_mean >= 0) %>%
  group_by(monitor_day) %>%
  summarize(pm2.5_concentration_daily_mean = 
              mean(pm2.5_concentration_daily_mean)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(pm2.5_concentration_daily_mean >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(pm2.5_concentration_daily_mean >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Unadjusted (crude) linear regression model

```{r echo=FALSE}
model_fit <- felm(pm2.5_concentration_daily_mean ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                  data = data_in)
summary(model_fit)
```

#### Adjusted linear regression model + month + basin:year FE

*Without* a monitor FE

```{r echo=FALSE}
model_fit <- felm(pm2.5_concentration_daily_mean ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    wells_dw_new_0to1km +
                    wells_dw_new_1to2km +
                    wells_dw_new_2to3km +
                    wells_dw_new_3to4km +
                    wells_dw_new_4to5km +
                    wells_dw_new_5to6km +
                    wells_dw_new_6to7km +
                    wells_dw_new_7to8km +
                    wells_dw_new_8to9km +
                    wells_dw_new_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

#### Adjusted linear regression model with monitor + month + basin:year FE adjusted for temp + precip

```{r echo=FALSE}
model_fit <- felm(pm2.5_concentration_daily_mean ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    wells_dw_new_0to1km +
                    wells_dw_new_1to2km +
                    wells_dw_new_2to3km +
                    wells_dw_new_3to4km +
                    wells_dw_new_4to5km +
                    wells_dw_new_5to6km +
                    wells_dw_new_6to7km +
                    wells_dw_new_7to8km +
                    wells_dw_new_8to9km +
                    wells_dw_new_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Upwind wells**

*Table*

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[24:33]
  )
saveRDS(model_output, file = "upwind_preprod_pm_pm25.rds")
model_output
```

*Figure*

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily PM2.5 conc. (µg/m^3)") +
  theme_classic()
```

**Downwind wells**

*Table*

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Downwind",
    point_est = coef(model_fit)[11:20],
    ci_lower  = confint(model_fit)[11:20],
    ci_upper  = confint(model_fit)[34:43]
  )
model_output
saveRDS(model_output, file = "downwind_preprod_pm_pm25.rds")
```

*Figure*

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily PM2.5 conc. (µg/m^3)") +
  theme_classic()
```


**Count of new wells within 1-km bins of PM2.5 monitors**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(pm2.5_concentration_daily_mean >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "Distance from monitor (km)", y = "n wells") +
  theme_classic()
```


## Pollutant: PM2.5 Arsenic

```{r include=FALSE}
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(pm25_as >= 0) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-pm25_as)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(pm25_as >= 0) %>%
  group_by(monitor_day) %>%
  summarize(pm25_as = 
              mean(pm25_as)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(pm25_as >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(pm25_as >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(pm25_as ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[14:23]
  )
model_output
saveRDS(model_output, file = "upwind_new_pm25_as.rds")
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily ethylbenzene (units)") +
  theme_classic()
```

**Count of new wells within 1-km bins of monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(pm25_as >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "Distance from monitor (km)", y = "n wells") +
  theme_classic()
```


## Pollutant: PM2.5 Lead

```{r include=FALSE}
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(pm25_pb >= 0) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-pm25_pb)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(pm25_pb >= 0) %>%
  group_by(monitor_day) %>%
  summarize(pm25_pb = 
              mean(pm25_pb)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(pm25_pb >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(pm25_pb >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(pm25_pb ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[14:23]
  )
model_output
saveRDS(model_output, file = "upwind_new_pm25_pb.rds")
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily ethylbenzene (units)") +
  theme_classic()
```

**Count of new wells within 1-km bins of monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(pm25_pb >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "Distance from monitor (km)", y = "n wells") +
  theme_classic()
```


# VOCs

## Pollutant: Total NMOC

```{r include=FALSE}
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(total_nmoc >= 0) %>%
  inner_join(aqs_daily_annuli_preproduction_dw) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-total_nmoc)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(total_nmoc >= 0) %>%
  group_by(monitor_day) %>%
  summarize(total_nmoc = 
              mean(total_nmoc)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(total_nmoc >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(total_nmoc >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(total_nmoc ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    wells_dw_new_0to1km +
                    wells_dw_new_1to2km +
                    wells_dw_new_2to3km +
                    wells_dw_new_3to4km +
                    wells_dw_new_4to5km +
                    wells_dw_new_5to6km +
                    wells_dw_new_6to7km +
                    wells_dw_new_7to8km +
                    wells_dw_new_8to9km +
                    wells_dw_new_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Upwind**

*Table*

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[24:33]
  )
saveRDS(model_output, file = "upwind_preprod_vocs_nmoc.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily NMOC (units)") +
  theme_classic()
```

**Downwind**

*Table*

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Downwind",
    point_est = coef(model_fit)[11:20],
    ci_lower  = confint(model_fit)[11:20],
    ci_upper  = confint(model_fit)[34:43]
  )
saveRDS(model_output, file = "downwind_preprod_vocs_nmoc.rds")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily NMOC (units)") +
  theme_classic()
```


**Count of new wells within 1-km bins of monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(total_nmoc >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
figure_3b <- well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "", y = "") +
  scale_y_continuous(position = "right") +
  theme_classic() +
  theme(axis.line    = element_blank(),  # removes x-axis
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
figure_3b

ggsave(filename = "figure_3b_vocs_nmoc.png", 
       plot = figure_3b, device = "png",
       height = 1, width = 7,
       path = "../../output/figures/")
```


## Pollutant: Acetaldehyde

```{r include=FALSE}
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(acetaldehyde >= 0) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-acetaldehyde)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(acetaldehyde >= 0) %>%
  group_by(monitor_day) %>%
  summarize(acetaldehyde = 
              mean(acetaldehyde)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(acetaldehyde >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(acetaldehyde >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(acetaldehyde ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[14:23]
  )
model_output
saveRDS(model_output, file = "upwind_new_voc_acetaldehyde.rds")
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily acetaldehyde (units)") +
  theme_classic()
```

**Count of new wells within 1-km bins of CO monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(acetaldehyde >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "Distance from monitor (km)", y = "n wells") +
  theme_classic()
```


## Pollutant: Acetone

```{r include=FALSE}
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(acetone >= 0) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-acetone)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(acetone >= 0) %>%
  group_by(monitor_day) %>%
  summarize(acetone = 
              mean(acetone)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(acetone >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(acetone >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(acetone ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[14:23]
  )
model_output
saveRDS(model_output, file = "upwind_new_voc_acetone.rds")
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily NMOC (units)") +
  theme_classic()
```

**Count of new wells within 1-km bins of monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(acetone >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "Distance from monitor (km)", y = "n wells") +
  theme_classic()
```


## Pollutant: Benzene

```{r include=FALSE}
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(benzene >= 0) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-benzene)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(benzene >= 0) %>%
  group_by(monitor_day) %>%
  summarize(benzene = 
              mean(benzene)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(benzene >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(benzene >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(benzene ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[14:23]
  )
model_output
saveRDS(model_output, file = "upwind_new_voc_benzene.rds")
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily NMOC (units)") +
  theme_classic()
```

**Count of new wells within 1-km bins of CO monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(benzene >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "Distance from monitor (km)", y = "n wells") +
  theme_classic()
```


## Pollutant: Dichloromethane

```{r include=FALSE}
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(dichloromethane >= 0) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-dichloromethane)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(dichloromethane >= 0) %>%
  group_by(monitor_day) %>%
  summarize(dichloromethane = 
              mean(dichloromethane)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(dichloromethane >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(dichloromethane >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(dichloromethane ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[14:23]
  )
model_output
saveRDS(model_output, file = "upwind_new_voc_dichloromethane.rds")
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily dichloromethane (units)") +
  theme_classic()
```

**Count of new wells within 1-km bins of monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(dichloromethane >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "Distance from monitor (km)", y = "n wells") +
  theme_classic()
```


## Pollutant: Ethylbenzene

```{r include=FALSE}
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(ethylbenzene >= 0) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-ethylbenzene)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(ethylbenzene >= 0) %>%
  group_by(monitor_day) %>%
  summarize(ethylbenzene = 
              mean(ethylbenzene)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(ethylbenzene >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(ethylbenzene >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(ethylbenzene ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[14:23]
  )
model_output
saveRDS(model_output, file = "upwind_new_voc_ethylbenzene.rds")
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily ethylbenzene (units)") +
  theme_classic()
```

**Count of new wells within 1-km bins of monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(ethylbenzene >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "Distance from monitor (km)", y = "n wells") +
  theme_classic()
```


## Pollutant: Formaldehyde

```{r include=FALSE}
covars <- aqs_daily_annuli_preproduction_uw %>%
  filter(formaldehyde >= 0) %>%
  distinct(monitor_day, .keep_all = TRUE) %>%
  select(-formaldehyde)
data_in <- aqs_daily_annuli_preproduction_uw %>%
  filter(formaldehyde >= 0) %>%
  group_by(monitor_day) %>%
  summarize(formaldehyde = 
              mean(formaldehyde)) %>%
  left_join(covars, by = "monitor_day")
```

Descriptive statistics:

- n monitor days = `r aqs_daily_annuli_preproduction_uw %>% filter(benzene >= 0) %>% distinct(monitor_day) %>% nrow()`
- n monitors in analytic data = `r aqs_daily_annuli_preproduction_uw %>% filter(benzene >= 0) %>% distinct(monitor_id) %>% nrow()`

#### Linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(formaldehyde ~ 
                    wells_new_0to1km +
                    wells_new_1to2km +
                    wells_new_2to3km +
                    wells_new_3to4km +
                    wells_new_4to5km +
                    wells_new_5to6km +
                    wells_new_6to7km +
                    wells_new_7to8km +
                    wells_new_8to9km +
                    wells_new_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | monitor_id + 
                    factor(month(date)) +
                    factor(carb_basin):factor(year(date)),
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = "Upwind",
    point_est = coef(model_fit)[1:10],
    ci_lower  = confint(model_fit)[1:10],
    ci_upper  = confint(model_fit)[14:23]
  )
model_output
saveRDS(model_output, file = "upwind_new_voc_formaldehyde.rds")
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily formaldehyde (units)") +
  theme_classic()
```

**Count of new wells within 1-km bins of monitor**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# selects monitors
monitor_points <- aqs_daily_annuli_preproduction_uw %>% 
  filter(formaldehyde >= 0) %>% 
  distinct(monitor_id, .keep_all = TRUE) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83)

# makes 1-km annuli around all relevant monitors
annulus0to1 <- monitor_points %>%
  st_transform(crs_projected) %>%
  st_buffer(dist = 1000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus1to2 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 2000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus2to3 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 3000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus3to4 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 4000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus4to5 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 5000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus5to6 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 6000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus6to7 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 7000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus7to8 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 8000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus8to9 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 9000) %>%
  st_union() %>%
  st_transform(crs_nad83)
annulus9to10 <- monitor_points %>% 
  st_transform(crs_projected) %>%
  st_buffer(dist = 10000) %>%
  st_union() %>%
  st_transform(crs_nad83)

# finalizes annuli by successively clipping differences in reverse order
annulus9to10  <- st_difference(annulus9to10,  annulus8to9)
annulus8to9   <- st_difference(annulus8to9,   annulus7to8)
annulus7to8   <- st_difference(annulus7to8,   annulus6to7)
annulus6to7   <- st_difference(annulus6to7,   annulus5to6)
annulus5to6   <- st_difference(annulus5to6,   annulus4to5)
annulus4to5   <- st_difference(annulus4to5,   annulus3to4)
annulus3to4   <- st_difference(annulus3to4,   annulus2to3)
annulus2to3   <- st_difference(annulus2to3,   annulus1to2)
annulus1to2   <- st_difference(annulus1to2,   annulus0to1)

# counts wells within each buffer
well_sum <- 
  tibble(
    wells_0to1  = sum(unlist(st_intersects(wells_sf, annulus0to1))),
    wells_1to2  = sum(unlist(st_intersects(wells_sf, annulus1to2))),
    wells_2to3  = sum(unlist(st_intersects(wells_sf, annulus2to3))),
    wells_3to4  = sum(unlist(st_intersects(wells_sf, annulus3to4))),
    wells_4to5  = sum(unlist(st_intersects(wells_sf, annulus4to5))),
    wells_5to6  = sum(unlist(st_intersects(wells_sf, annulus5to6))),
    wells_6to7  = sum(unlist(st_intersects(wells_sf, annulus6to7))),
    wells_7to8  = sum(unlist(st_intersects(wells_sf, annulus7to8))),
    wells_8to9  = sum(unlist(st_intersects(wells_sf, annulus8to9))),
    wells_9to10 = sum(unlist(st_intersects(wells_sf, annulus9to10)))
  ) %>%
  pivot_longer(wells_0to1:wells_9to10, names_to = "bin", values_to = "count") %>%
  mutate(distance = c("0-1", "1-2", "2-3", "3-4", "4-5",
                      "5-6", "6-7", "7-8", "8-9", "9-10"))
```

```{r echo=FALSE}
figure_3b <- well_sum %>%
  ggplot() + 
  geom_bar(aes(as.factor(distance), count), stat = "identity") + 
  labs(x = "", y = "") +
  scale_y_continuous(position = "right") +
  theme_classic() +
  theme(axis.line    = element_blank(),  # removes x-axis
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
figure_3b

ggsave(filename = "figure_3b_upwind_vocs_formaldehyde.png", 
       plot = figure_3b, device = "png",
       height = 1, width = 7,
       path = "../../output/figures/")
```



