---
title: "Ch. 3: Oil production and ambient air quality in California"
subtitle: "Results - Monthly IDW New Wells"
output: html_notebook
---

```{r setup, include=FALSE}
source("../../code/0-setup/1-setup.R")
library("lfe")
```

```{r data_import, include=FALSE}
aqs_exposure_idw_preprod <- 
  readRDS("../../data/interim/aqs_exposure_monthly_idw_nowind_preprod.rds")
aqs_exposure_idw_prod <- 
  readRDS("../../data/interim/aqs_exposure_monthly_idw_nowind_prod.rds")
carb_basin <- 
  st_read("../../data/raw/cal_epa/carb_air_basins/CaAirBasin.shp") %>%
  st_transform(crs_nad83)
wells_interim <- readRDS("../../data/interim/wells_interim.rds")
cal_counties_raw <- 
  st_read("../../data/raw/us_census/admin_shp/cal_counties.shp")
```

```{r data_tidying, include=FALSE}
# bins IDW index into exposure quartiles
source("../../code/2-exposure_assessment/3-make_idw_exposure_quantiles.R")
aqs_exposure_idw_preprod <- makeExposureQuantiles(aqs_exposure_idw_preprod,
                                                  "idw_index",
                                                  "exp_quartile", 
                                                  4)

# appends CARB air basin to the dataset
aqs_basins <- read_csv("../../data/interim/aqs_sites.csv") %>% 
  st_as_sf(coords = c("longitude", "latitude"), crs = crs_nad83) %>%
  st_join(carb_basin) %>%
  as_tibble() %>%
  select(site_id, NAME) %>%
  rename(carb_basin = NAME)
aqs_exposure_idw_preprod <- aqs_exposure_idw_preprod %>%
  left_join(aqs_basins, by = "site_id")
```

## Pollutant: CO

**Notes:**

- We used data from `r aqs_exposure_idw_preprod %>% filter(monthly_mean_co > 0) %>% distinct(site_id) %>% nrow()` monitors and `r aqs_exposure_idw_preprod %>% filter(monthly_mean_co > 0) %>% distinct(site_id_month_year) %>% nrow()` monitor-months, from `r min(aqs_exposure_idw_preprod$month_year)` to `r max(aqs_exposure_idw_preprod$month_year)`
- We droppped the `r aqs_exposure_idw_preprod %>% filter(monthly_mean_co <= 0) %>% nrow()` monitor-months that had nonsensical mean monthly CO concentrations of ≤ 0 µg/m^3, 

#### Crude model

```{r echo=FALSE}
model_fit <- felm(monthly_mean_co ~ 
                    as.factor(exp_quartile),
                  data = subset(aqs_exposure_idw_preprod, 
                                monthly_mean_co > 0))
summary(model_fit)
```

#### FE for air basin:month + year

```{r echo=FALSE}
model_fit <- felm(monthly_mean_co ~ 
                    as.factor(exp_quartile) 
                  | factor(carb_basin):factor(month(month_year)) +
                    factor(year(month_year)),
                  data = subset(aqs_exposure_idw_preprod, 
                                monthly_mean_co > 0))
summary(model_fit)
```

#### FE for monitor + air basin-month + year

```{r echo=FALSE}
model_fit <- felm(monthly_mean_co ~
                    as.factor(exp_quartile) 
                  | factor(site_id) +
                    factor(carb_basin):factor(month(month_year)) +
                    factor(year(month_year)),
                  data = subset(drop_na(aqs_exposure_idw_preprod,
                                        monthly_mean_co), 
                                monthly_mean_so2 > 0))
summary(model_fit)
```


## Pollutant: NO2

**Notes:**

- We used data from `r aqs_exposure_idw_preprod %>% filter(monthly_mean_no2 > 0) %>% distinct(site_id) %>% nrow()` monitors and `r aqs_exposure_idw_preprod %>% filter(monthly_mean_no2 > 0) %>% distinct(site_id_month_year) %>% nrow()` monitor-months, from `r min(aqs_exposure_idw_preprod$month_year)` to `r max(aqs_exposure_idw_preprod$month_year)`
- We droppped the `r aqs_exposure_idw_preprod %>% filter(monthly_mean_no2 <= 0) %>% nrow()` monitor-months that had nonsensical mean monthly NO2 concentrations of ≤ 0 µg/m^3, 

#### Crude model

```{r echo=FALSE}
model_fit <- felm(monthly_mean_no2 ~ 
                    as.factor(exp_quartile),
                  data = subset(aqs_exposure_idw_preprod, 
                                monthly_mean_no2 > 0))
summary(model_fit)
```

#### FE for air basin:month + year

```{r echo=FALSE}
model_fit <- felm(monthly_mean_no2 ~ 
                    as.factor(exp_quartile) 
                  | factor(carb_basin):factor(month(month_year)) +
                    factor(year(month_year)),
                  data = subset(aqs_exposure_idw_preprod, 
                                monthly_mean_no2 > 0))
summary(model_fit)
```

#### FE for monitor + air basin-month + year

```{r echo=FALSE}
model_fit <- felm(monthly_mean_no2 ~
                    as.factor(exp_quartile) 
                  | factor(site_id) +
                    factor(carb_basin):factor(month(month_year)) +
                    factor(year(month_year)),
                  data = subset(drop_na(aqs_exposure_idw_preprod,
                                        monthly_mean_no2), 
                                monthly_mean_so2 > 0))
summary(model_fit)
```


## Pollutant: O3

**Notes:**

- We used data from `r aqs_exposure_idw_preprod %>% filter(monthly_mean_ozone > 0) %>% distinct(site_id) %>% nrow()` monitors and `r aqs_exposure_idw_preprod %>% filter(monthly_mean_ozone > 0) %>% distinct(site_id_month_year) %>% nrow()` monitor-months, from `r min(aqs_exposure_idw_preprod$month_year)` to `r max(aqs_exposure_idw_preprod$month_year)`
- We droppped the `r aqs_exposure_idw_preprod %>% filter(monthly_mean_ozone <= 0) %>% nrow()` monitor-months that had nonsensical mean monthly O3 concentrations of ≤ 0 µg/m^3, 

#### Crude model

```{r echo=FALSE}
model_fit <- felm(monthly_mean_ozone ~ 
                    as.factor(exp_quartile),
                  data = subset(aqs_exposure_idw_preprod, 
                                monthly_mean_ozone > 0))
summary(model_fit)
```

#### FE for air basin:month + year

```{r echo=FALSE}
model_fit <- felm(monthly_mean_ozone ~ 
                    as.factor(exp_quartile) 
                  | factor(carb_basin):factor(month(month_year)) +
                    factor(year(month_year)),
                  data = subset(aqs_exposure_idw_preprod, 
                                monthly_mean_ozone > 0))
summary(model_fit)
```

#### FE for monitor + air basin-month + year

```{r echo=FALSE}
model_fit <- felm(monthly_mean_ozone ~
                    as.factor(exp_quartile) 
                  | factor(site_id) +
                    factor(carb_basin):factor(month(month_year)) +
                    factor(year(month_year)),
                  data = subset(drop_na(aqs_exposure_idw_preprod,
                                        monthly_mean_ozone), 
                                monthly_mean_ozone > 0))
summary(model_fit)
```

## Pollutant: PM2.5

**Notes:**

- We used data from `r aqs_exposure_idw_preprod %>% filter(monthly_mean_pm2.5 > 0) %>% distinct(site_id) %>% nrow()` monitors and `r aqs_exposure_idw_preprod %>% filter(monthly_mean_pm2.5 > 0) %>% distinct(site_id_month_year) %>% nrow()` monitor-months, from `r min(aqs_exposure_idw_preprod$month_year)` to `r max(aqs_exposure_idw_preprod$month_year)`
- We droppped the `r aqs_exposure_idw_preprod %>% filter(monthly_mean_pm2.5 <= 0) %>% nrow()` monitor-months that had nonsensical mean monthly PM2.5 concentrations of ≤ 0 µg/m^3, 

#### Crude model

```{r echo=FALSE}
model_fit <- felm(monthly_mean_pm2.5 ~ 
                    as.factor(exp_quartile),
                  data = subset(aqs_exposure_idw_preprod, 
                                monthly_mean_pm2.5 > 0))
summary(model_fit)
```

#### FE for air basin:month + year

```{r echo=FALSE}
model_fit <- felm(monthly_mean_pm2.5 ~ 
                    as.factor(exp_quartile) 
                  | factor(carb_basin):factor(month(month_year)) +
                    factor(year(month_year)),
                  data = subset(aqs_exposure_idw_preprod, 
                                monthly_mean_pm2.5 > 0))
summary(model_fit)
```

#### FE for monitor + air basin-month + year

```{r echo=FALSE}
model_fit <- felm(monthly_mean_pm2.5 ~
                    as.factor(exp_quartile) 
                  | factor(site_id) +
                    factor(carb_basin):factor(month(month_year)) +
                    factor(year(month_year)),
                  data = subset(drop_na(aqs_exposure_idw_preprod,
                                        monthly_mean_pm2.5), 
                                monthly_mean_pm2.5 > 0))
summary(model_fit)
```


## Pollutant: PM10

**Notes:**

- We used data from `r aqs_exposure_idw_preprod %>% filter(monthly_mean_pm10 > 0) %>% distinct(site_id) %>% nrow()` monitors and `r aqs_exposure_idw_preprod %>% filter(monthly_mean_pm10 > 0) %>% distinct(site_id_month_year) %>% nrow()` monitor-months, from `r min(aqs_exposure_idw_preprod$month_year)` to `r max(aqs_exposure_idw_preprod$month_year)`
- We droppped the `r aqs_exposure_idw_preprod %>% filter(monthly_mean_pm10 <= 0) %>% nrow()` monitor-months that had nonsensical mean monthly PM10 concentrations of ≤ 0 µg/m^3, 

#### Crude model

```{r echo=FALSE}
model_fit <- felm(monthly_mean_pm10 ~ 
                    as.factor(exp_quartile),
                  data = subset(aqs_exposure_idw_preprod, 
                                monthly_mean_pm10 > 0))
summary(model_fit)
```

#### FE for air basin:month + year

```{r echo=FALSE}
model_fit <- felm(monthly_mean_pm10 ~ 
                    as.factor(exp_quartile) 
                  | factor(carb_basin):factor(month(month_year)) +
                    factor(year(month_year)),
                  data = subset(aqs_exposure_idw_preprod, 
                                monthly_mean_pm10 > 0))
summary(model_fit)
```

#### FE for monitor + air basin-month + year

```{r echo=FALSE}
model_fit <- felm(monthly_mean_pm10 ~
                    as.factor(exp_quartile) 
                  | factor(site_id) +
                    factor(carb_basin):factor(month(month_year)) +
                    factor(year(month_year)),
                  data = subset(drop_na(aqs_exposure_idw_preprod,
                                        monthly_mean_pm10), 
                                monthly_mean_pm10 > 0))
summary(model_fit)
```

## Pollutant: SO2

**Notes:**

- We used data from `r aqs_exposure_idw_preprod %>% filter(monthly_mean_so2 > 0) %>% distinct(site_id) %>% nrow()` monitors and `r aqs_exposure_idw_preprod %>% filter(monthly_mean_so2 > 0) %>% distinct(site_id_month_year) %>% nrow()` monitor-months, from `r min(aqs_exposure_idw_preprod$month_year)` to `r max(aqs_exposure_idw_preprod$month_year)`
- We droppped the `r aqs_exposure_idw_preprod %>% filter(monthly_mean_so2 <= 0) %>% nrow()` monitor-months that had nonsensical mean monthly SO2 concentrations of ≤ 0 µg/m^3, 

#### Crude model

```{r echo=FALSE}
model_fit <- felm(monthly_mean_so2 ~ 
                    as.factor(exp_quartile),
                  data = subset(aqs_exposure_idw_preprod, 
                                monthly_mean_so2 > 0))
summary(model_fit)
```

#### FE for air basin:month + year

```{r echo=FALSE}
model_fit <- felm(monthly_mean_so2 ~ 
                    as.factor(exp_quartile) 
                  | factor(carb_basin):factor(month(month_year)) +
                    factor(year(month_year)),
                  data = subset(aqs_exposure_idw_preprod, 
                                monthly_mean_so2 > 0))
summary(model_fit)
```

#### FE for monitor + air basin-month + year

```{r echo=FALSE}
model_fit <- felm(monthly_mean_so2 ~
                    as.factor(exp_quartile) 
                  | factor(site_id) +
                    factor(carb_basin):factor(month(month_year)) +
                    factor(year(month_year)),
                  data = subset(drop_na(aqs_exposure_idw_preprod,
                                        monthly_mean_so2), 
                                monthly_mean_so2 > 0))
summary(model_fit)
```