---
title: "Results - Daily Annuli - Production - VOCs"
output: html_notebook
---

*add prelimn exposure assessments for prod volume*

```{r setup, include=FALSE}
source("../../code/0-setup/1-setup.R")
library("lfe")
```

```{r input_data, include=FALSE}
aqs_daily_annuli_exposure <- 
  readRDS("../../data/processed/aqs_daily_annuli_exposure.rds")
```

```{r setup_data, include=FALSE}
data_in <- aqs_daily_annuli_exposure %>%
  filter(vocs_total >= 0) #%>%
  #filter(year %in% c(2006:2019))
```

### Primary Analysis

#### Unadjusted linear model without FE

```{r echo=FALSE}
model_fit <- glm(vocs_total ~ 
                   prod_volume_upwind_0to1km +
                   prod_volume_upwind_1to2km +
                   prod_volume_upwind_2to3km +
                   prod_volume_upwind_3to4km +
                   prod_volume_upwind_4to5km +
                   prod_volume_upwind_5to6km +
                   prod_volume_upwind_6to7km +
                   prod_volume_upwind_7to8km +
                   prod_volume_upwind_8to9km +
                   prod_volume_upwind_9to10km +
                   prod_volume_downwind_0to1km +
                   prod_volume_downwind_1to2km +
                   prod_volume_downwind_2to3km +
                   prod_volume_downwind_3to4km +
                   prod_volume_downwind_4to5km +
                   prod_volume_downwind_5to6km +
                   prod_volume_downwind_6to7km +
                   prod_volume_downwind_7to8km +
                   prod_volume_downwind_8to9km +
                   prod_volume_downwind_9to10km +
                   prod_volume_lateral_0to1km +
                   prod_volume_lateral_1to2km +
                   prod_volume_lateral_2to3km +
                   prod_volume_lateral_3to4km +
                   prod_volume_lateral_4to5km +
                   prod_volume_lateral_5to6km +
                   prod_volume_lateral_6to7km +
                   prod_volume_lateral_7to8km +
                   prod_volume_lateral_8to9km +
                   prod_volume_lateral_9to10km,
                 data = data_in)
summary(model_fit)
```

#### Adjusted linear model without FE

```{r echo=FALSE}
model_fit <- felm(vocs_total ~ 
                    prod_volume_upwind_0to1km +
                    prod_volume_upwind_1to2km +
                    prod_volume_upwind_2to3km +
                    prod_volume_upwind_3to4km +
                    prod_volume_upwind_4to5km +
                    prod_volume_upwind_5to6km +
                    prod_volume_upwind_6to7km +
                    prod_volume_upwind_7to8km +
                    prod_volume_upwind_8to9km +
                    prod_volume_upwind_9to10km +
                    prod_volume_downwind_0to1km +
                    prod_volume_downwind_1to2km +
                    prod_volume_downwind_2to3km +
                    prod_volume_downwind_3to4km +
                    prod_volume_downwind_4to5km +
                    prod_volume_downwind_5to6km +
                    prod_volume_downwind_6to7km +
                    prod_volume_downwind_7to8km +
                    prod_volume_downwind_8to9km +
                    prod_volume_downwind_9to10km +
                    prod_volume_lateral_0to1km +
                    prod_volume_lateral_1to2km +
                    prod_volume_lateral_2to3km +
                    prod_volume_lateral_3to4km +
                    prod_volume_lateral_4to5km +
                    prod_volume_lateral_5to6km +
                    prod_volume_lateral_6to7km +
                    prod_volume_lateral_7to8km +
                    prod_volume_lateral_8to9km +
                    prod_volume_lateral_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | day_of_week,
                  data = data_in)
summary(model_fit)
```

#### Adjusted linear model with month and basin:year FE

```{r echo=FALSE}
model_fit <- felm(vocs_total ~ 
                    prod_volume_upwind_0to1km +
                    prod_volume_upwind_1to2km +
                    prod_volume_upwind_2to3km +
                    prod_volume_upwind_3to4km +
                    prod_volume_upwind_4to5km +
                    prod_volume_upwind_5to6km +
                    prod_volume_upwind_6to7km +
                    prod_volume_upwind_7to8km +
                    prod_volume_upwind_8to9km +
                    prod_volume_upwind_9to10km +
                    prod_volume_downwind_0to1km +
                    prod_volume_downwind_1to2km +
                    prod_volume_downwind_2to3km +
                    prod_volume_downwind_3to4km +
                    prod_volume_downwind_4to5km +
                    prod_volume_downwind_5to6km +
                    prod_volume_downwind_6to7km +
                    prod_volume_downwind_7to8km +
                    prod_volume_downwind_8to9km +
                    prod_volume_downwind_9to10km +
                    prod_volume_lateral_0to1km +
                    prod_volume_lateral_1to2km +
                    prod_volume_lateral_2to3km +
                    prod_volume_lateral_3to4km +
                    prod_volume_lateral_4to5km +
                    prod_volume_lateral_5to6km +
                    prod_volume_lateral_6to7km +
                    prod_volume_lateral_7to8km +
                    prod_volume_lateral_8to9km +
                    prod_volume_lateral_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed
                  | day_of_week + 
                    factor(monitor_id):factor(month) +
                    factor(carb_basin):factor(year),
                  data = data_in)
summary(model_fit)
```


#### Adjust linear model with monitor + month + basin:year FE

**Primary analysis**

```{r echo=FALSE}
model_fit <- felm(vocs_total ~ 
                    prod_volume_upwind_0to1km +
                    prod_volume_upwind_1to2km +
                    prod_volume_upwind_2to3km +
                    prod_volume_upwind_3to4km +
                    prod_volume_upwind_4to5km +
                    prod_volume_upwind_5to6km +
                    prod_volume_upwind_6to7km +
                    prod_volume_upwind_7to8km +
                    prod_volume_upwind_8to9km +
                    prod_volume_upwind_9to10km +
                    prod_volume_downwind_0to1km +
                    prod_volume_downwind_1to2km +
                    prod_volume_downwind_2to3km +
                    prod_volume_downwind_3to4km +
                    prod_volume_downwind_4to5km +
                    prod_volume_downwind_5to6km +
                    prod_volume_downwind_6to7km +
                    prod_volume_downwind_7to8km +
                    prod_volume_downwind_8to9km +
                    prod_volume_downwind_9to10km +
                    prod_volume_lateral_0to1km +
                    prod_volume_lateral_1to2km +
                    prod_volume_lateral_2to3km +
                    prod_volume_lateral_3to4km +
                    prod_volume_lateral_4to5km +
                    prod_volume_lateral_5to6km +
                    prod_volume_lateral_6to7km +
                    prod_volume_lateral_7to8km +
                    prod_volume_lateral_8to9km +
                    prod_volume_lateral_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed +
                    n_plume
                  | day_of_week + 
                    factor(carb_basin):factor(month) +
                    factor(carb_basin):factor(year) +
                    monitor_id,
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10",
                  "0-1", "1-2", "2-3", "3-4", "4-5",
                  "5-6", "6-7", "7-8", "8-9", "9-10"),
    direction = c("Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Upwind", "Upwind", "Upwind", "Upwind", "Upwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Downwind", "Downwind", "Downwind", "Downwind", "Downwind",
                  "Lateral", "Lateral", "Lateral", "Lateral","Lateral",
                  "Lateral", "Lateral", "Lateral", "Lateral","Lateral"),
    point_est = coef(model_fit)[1:30],
    ci_lower  = confint(model_fit)[1:30],
    ci_upper  = confint(model_fit)[35:64])
write_csv(model_output, "point_estimates/daily_annuli_production_voc.csv")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper),
                  alpha = 0.5) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily VOC conc. (ppb C)") +
  theme_classic() +
  facet_wrap(~ direction)
```


## No wind

#### Adjust linear model with monitor + month + basin:year FE

```{r echo=FALSE}
model_fit <- felm(vocs_total ~ 
                    prod_volume_nowind_0to1km +
                    prod_volume_nowind_1to2km +
                    prod_volume_nowind_2to3km +
                    prod_volume_nowind_3to4km +
                    prod_volume_nowind_4to5km +
                    prod_volume_nowind_5to6km +
                    prod_volume_nowind_6to7km +
                    prod_volume_nowind_7to8km +
                    prod_volume_nowind_8to9km +
                    prod_volume_nowind_9to10km +
                    narr_precip + 
                    narr_temp +
                    narr_wind_speed +
                    n_plume
                  | day_of_week + 
                    factor(monitor_id):factor(month) +
                    factor(carb_basin):factor(year) +
                    monitor_id,
                  data = data_in)
summary(model_fit)
```

**Table**

```{r echo=FALSE}
model_output <-
  tibble(
    distance  = c("0-1", "1-2", "2-3", "3-4", "4-5"),
    point_est = coef(model_fit)[1:5],
    ci_lower  = confint(model_fit)[1:5],
    ci_upper  = confint(model_fit)[15:19])
write_csv(model_output, "point_estimates/daily_annuli_production_vocs_nowind.csv")
model_output
```

**Figure**

```{r echo=FALSE, warning = FALSE}
model_output %>%
  ggplot() + 
  geom_pointrange(aes(x = distance, y = point_est, 
                      ymin = ci_lower, ymax = ci_upper),
                  alpha = 0.5) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Distance to well (km)", 
       y = "Marginal change in daily PM2.5 conc. (µg/m^3)") +
  theme_classic()
```


#### Adjust linear model with monitor + month + basin:year FE - 60°

*Note: See memo from March 2021 for this analysis*